---
title: "Cough Project Main File"
author: "Raphael Kroes"
date: "2023-12-07"
output: html_document
---


```{r}
library(readxl)
library(dplyr)
library(parallel)
library(lubridate)
library(ggplot2)
library(writexl)
```

```{r}
# Read in data
real.data<- TRUE
if(real.data){
  setwd("N:/StudentischeHilfskraefte/_Kroes (Christoph)/Routinedaten/01_Husten/R/DBnew2")
  names.vec<- c("Diag","ICPC","Labor","Stamm","Ueberweis", "PZN")

  for (i in seq(1,length(names.vec))) {
    file.name<- paste0("DB_",names.vec[i],"1_v03",".csv")
    im.file<- read.csv(file = file.name, header = TRUE, sep = ";")
    assign(names.vec[i],im.file)
  }
  rm(file.name,im.file)

  # Read in supplementary data
  ListeKrankenkassen<- read.csv("https://github.com/rapkroes/Code_UKSH_Husten/raw/main/ListeKrankenkassen.csv", sep = ";")
  altersstruktur_deutschland<- read.csv("https://github.com/rapkroes/Code_UKSH_Husten/raw/main/altersstruktur%20deutschland.csv", sep = ";")
  colnames(altersstruktur_deutschland)<- c("altersjahre","bevoelkerungsstand")
  icd10_blocks<- read.csv("https://github.com/rapkroes/Code_UKSH_Husten/raw/main/icd10_blocks.csv", sep = ";")
  icd10_description<- read.csv("https://github.com/rapkroes/Code_UKSH_Husten/blob/288b25aa745f178d2705d990e5106ad6db320a4d/icd10_description.csv")
  selected.lab.descriptions<- read.csv("https://github.com/rapkroes/Code_UKSH_Husten/raw/main/freitextanalyse.csv", sep = ";")
  ICD3St<- read.csv("https://raw.githubusercontent.com/rapkroes/Code_UKSH_Husten/main/Table_ICD_3St.csv", sep = ";")
  source("//fileserver1.uni-luebeck.de/ifa_homes/raphaelkroes/Documents/GitHub/Code_UKSH_Husten/functions.R")

}else{
  source("fakedgp_work.R")
}
```

```{r}
diag.up<- Diag |> 
  select(uniPatID, TG_DateNum, Typ, icd10)|>
  distinct()
diag.up$chronic<- 0
diag.up$chronic[diag.up$chronic=="DD"]<- 1
diag.up$unipat_date<- paste(diag.up$uniPatID, diag.up$TG_DateNum, sep = "_")

#find patients with Chronic Pulmonary Obstructive Disease (COPD)
copd.vec<- unique(diag.up$uniPatID[grepl("J44", diag.up$icd10) | 
                              grepl("J 44", diag.up$icd10)])

# find all other chronically diseased people
im<- diag.up|>
  select(uniPatID, Typ, icd10)|>
  distinct()
chronic.patients<- im$uniPatID[im$Typ=="DD"]
chronic.patients<- as.data.frame(table(chronic.patients))
rm(im)
diag.up$chronic<- NULL

icpc.up<- ICPC |>
  select(uniPatID, TG_DateNum, TGTyp, icpc2)
icpc.up$unipat_date<- paste(icpc.up$uniPatID, icpc.up$TG_DateNum, sep = "_")

labor.up<- Labor
labor.up$labtest<- 1
labor.up<- labor.up|>
  select(uniPatID, TG_DateNum, Untersuchung, Unterstext, labtest)|>
  distinct()
colnames(selected.lab.descriptions)[1]<- "Unterstext"
labor.up<- left_join(labor.up, selected.lab.descriptions, by = "Unterstext")
labor.up$unipat_date<- paste(labor.up$uniPatID, labor.up$TG_DateNum, sep = "_")

stamm.up<- Stamm
stamm.up$PKV<- IK2PKV(stamm.up$IK)
stamm.up<- stamm.up|> 
  select(-PatID, -index_i, -IK, -Kasse, -PLZ)|>
  distinct()|>
  arrange(uniPatID,desc(TG_DateNum))
stamm.up$unipat_date<- paste(stamm.up$uniPatID, stamm.up$TG_DateNum, sep = "_")

ueberweis.up<- Ueberweis|>
  select(uniPatID, TG_DateNum, FR_Pneumo, FR_Radiol, FR_KH) |>
  filter(FR_Pneumo > 0 | FR_Radiol > 0 | FR_KH > 0) |>
  distinct()
ueberweis.up$unipat_date<- paste(ueberweis.up$uniPatID, ueberweis.up$TG_DateNum, sep = "_")

aub<- Diag|>
  filter(Typ == "AUB")|>
  select(uniPatID, TG_DateNum)
colnames(aub)[2]<- "TG_DateNum_AUB"

pzn.up<- PZN[substr(PZN$ATC, 1, 3) == "J01",]|>
  filter(TG == "ME")|>
  select(uniPatID, TG_DateNum)
colnames(pzn.up)[2]<- "TG_DateNum_antibiotic"
```


```{r}
# free up memory by clearing the original, raw datasets out
# rm(list = names.vec)
```

```{r}
# Do we have one entry per patient/ date combination?
length(unique(labor.up$unipat_date)) == nrow(labor.up)
length(unique(stamm.up$unipat_date)) == nrow(stamm.up)
length(unique(ueberweis.up$unipat_date)) == nrow(ueberweis.up)
length(unique(diag.up$unipat_date)) == nrow(diag.up)
length(unique(icpc.up$unipat_date)) == nrow(icpc.up)
```

STOP: Every patient/date combination must be unique. The difference between number of rows and patient/ time combinations must therefore be 0. This is what contains.multiple.entries checks for. We believe diag.up, icpc.up, and pzn.up have multiple entries for the same date by design. We believe stamm.up, labor.up, and ueberweis.up should have only one line per patient/ time combination. In #6.1 we remedy the presumed errors by selecting the last entry for each patient/ time combination. In #6.2 we write the multiple data points of diag.up, icpc.up, and pzn.up in additional columns. Both procedures leave us with unique date/ time combinations for each data set.
In #6.2, we do not keep all entries for diag.up and icpc.up. There are a few entries with unreasonably high numbers of diagnoses or symptoms. Therefore, we truncate the number observations at the 95% quantile of the distribution of entries per combination. If the last sentence is not clear in meaning, please run the commented code in chunk #6.2 to gain better insight.

```{r}
# Correcting labor.up, stamm.up, and ueberweis.up

labor.up<- data.repair.new(labor.up)
length(unique(labor.up$unipat_date)) == nrow(labor.up)

stamm.up<- data.repair.new(stamm.up)
length(unique(stamm.up$unipat_date)) == nrow(stamm.up)

ueberweis.up<- data.repair.new(ueberweis.up)
length(unique(ueberweis.up$unipat_date)) == nrow(ueberweis.up)
```

```{r}
# 5.2
cutoff_diag<- quantile(table(diag.up$unipat_date), probs= 0.95)

# table(paste0(diag.up$uniPatID,diag.up$TG_DateNum)
# quantile(table(paste0(diag.up$uniPatID,diag.up$TG_DateNum)))
diag.up_2<- aligner(diag.up, cutoff = cutoff_diag, var.name = "diag")
length(unique(diag.up_2$unipat_date)) == nrow(diag.up_2)

```

```{r}
# create episodes based on the data
selected.max.length.of.episode<- 21
episodes<- icpc.up|>
  filter(icpc2 == "R05")|>
  select(uniPatID, TG_DateNum)
colnames(episodes)[2]<- "start_date"
episodes$end_date<- episodes$start_date + selected.max.length.of.episode

```

There must be no overlap in the timing of the episodes in order to map diagnoses and treatments to the episodes.
There is no decision rule we can enforce that distinguishes perfectly whether episodes match or match not. Therefore, we implement different decision rules.

```{r}
# 7 create non-overlapping episodes

#decision rule 1: If the timing of episodes overlaps, we treat them as one episode
#decision rule 2: If the timing of episodes overlaps, we treat them as two distinct episodes. The last day of the earlier episode is the day before the new episode begins.

episodes_r1<- episodes.dr1(episodes)
episodes_r1$episode.ID<- paste0(episodes_r1$uniPatID, episodes_r1$start_date)
episodes_r2<- episodes.dr2(episodes)
episodes_r2$episode.ID<- paste0(episodes_r2$uniPatID, episodes_r2$start_date)

# test for how many overlaps there are
sum(episodes.overlap.finder(episodes_r1)$overlap)
sum(episodes.overlap.finder(episodes_r2)$overlap)
```

```{r}
#create complete datasets
episodes.stamm_r1<- add.stamm(episodes_r1, stamm.up, 100, 10)
episodes.diag_r1<- add.diag(episodes_r1, diag.up_2, 100, 10)
episodes.labor_r1<- add.lab(episodes_r1,labor.up)
episodes.ueberweis_1<- add.ueberweis(episodes_r1, ueberweis.up)
full_r1<- cbind(arrange(episodes.stamm_r1, uniPatID, start_date),
                arrange(episodes.diag_r1, uniPatID, start_date),
                arrange(episodes.labor_r1, uniPatID, start_date),
                arrange(episodes.ueberweis_1, uniPatID, start_date))
full_r1<- full_r1[,!duplicated(colnames(full_r1))]
full_r1$age<- year(TG_DateNum2date(full_r1$start_date)) - full_r1$Geburtsjahr
full_r1<- filter(full_r1, age <= 100)
full_r1$length_of_episode<- full_r1$end_date - full_r1$start_date

#same procedure for decision rule 2
episodes.stamm_r2<- add.stamm(episodes_r2, stamm.up, 100, 10)
episodes.diag_r2<- add.diag(episodes_r2, diag.up_2, 100, 10)
episodes.labor_r2<- add.lab(episodes_r2,labor.up)
episodes.ueberweis_2<- add.ueberweis(episodes_r2, ueberweis.up)
full_r2<- cbind(arrange(episodes.stamm_r2, uniPatID, start_date),
                arrange(episodes.diag_r2, uniPatID, start_date),
                arrange(episodes.labor_r2, uniPatID, start_date),
                arrange(episodes.ueberweis_2, uniPatID, start_date))
full_r2<- full_r2[,!duplicated(colnames(full_r2))]
full_r2$age<- year(TG_DateNum2date(full_r2$start_date)) - full_r2$Geburtsjahr
full_r2<- filter(full_r2, age <= 100)
full_r2$length_of_episode<- full_r2$end_date - full_r2$start_date

#no.chronic diseases 
colnames(chronic.patients)<- c("uniPatID", "no.chronic.diseases")
chronic.patients$uniPatID<- chronic.patients$uniPatID|>
  as.character()|>
  as.numeric()
full_r1<- left_join(full_r1, chronic.patients, by = "uniPatID")
full_r2<- left_join(full_r2, chronic.patients, by = "uniPatID")

for(k in 1:2){
  im<- get(paste0("full_r", k))
  
  #find cases where at least one initial diagnosis was preliminary
  first.cols<- grep("first_diag", colnames(im))
  last.cols<- grep("last_diag", colnames(im))
  
  im_first<- apply(im[,first.cols], 2, FUN = function(dv){
    im_dv<- substr(dv,nchar(dv),nchar(dv))
    return(grepl("V",im_dv))
  })
  im_last<- apply(im[,last.cols],2,FUN = function(dv){
    im_dv<- substr(dv,nchar(dv),nchar(dv))
    return(grepl("V",im_dv))
  })
  
  im$first_diag_V_present<- rowSums(im_first)>0
  im$last_diag_V_present<- rowSums(im_last)>0
  
  #add start month/ quarter
  im$start_month<- month(TG_DateNum2date(im$start_date))
  im$start_quarter<- quarter(TG_DateNum2date(im$start_date))
  
  assign(paste0("full_r",k),im)
  rm(im)
}

full_r1$FR_KH[full_r1$FR_KH == 0]<- NA
full_r1$FR_Pneumo[full_r1$FR_Pneumo == 0]<- NA
full_r1$FR_Radiol[full_r1$FR_Radiol == 0]<- NA

full_r2$FR_KH[full_r2$FR_KH == 0]<- NA
full_r2$FR_Pneumo[full_r2$FR_Pneumo == 0]<- NA
full_r2$FR_Radiol[full_r2$FR_Radiol == 0]<- NA

full_r1<- left_join(full_r1, aub, by = "uniPatID")
has.AUB<- full_r1$start_date <= full_r1$TG_DateNum_AUB & 
  full_r1$end_date >= full_r1$TG_DateNum_AUB
full_r1$TG_DateNum_AUB[!has.AUB]<- NA
full_r1<- arrange(full_r1, episode.ID, TG_DateNum_AUB)
episode.duplicate<- duplicated(full_r1$episode.ID)
full_r1<- full_r1[!episode.duplicate,]
full_r1$time_until_AUB<- full_r1$TG_DateNum_AUB - full_r1$start_date

full_r2<- left_join(full_r2, aub, by = "uniPatID")
has.AUB<- full_r2$start_date <= full_r2$TG_DateNum_AUB & 
  full_r2$end_date >= full_r2$TG_DateNum_AUB
full_r2$TG_DateNum_AUB[!has.AUB]<- NA
full_r2<- arrange(full_r2, episode.ID, TG_DateNum_AUB)
episode.duplicate<- duplicated(full_r2$episode.ID)
full_r2<- full_r2[!episode.duplicate,]
full_r2$time_until_AUB<- full_r2$TG_DateNum_AUB - full_r2$start_date

full_r1<- left_join(full_r1, pzn.up, by = "uniPatID")
has.PZN<- full_r1$start_date <= full_r1$TG_DateNum_antibiotic & 
  full_r1$end_date >= full_r1$TG_DateNum_antibiotic
full_r1$TG_DateNum_antibiotic[!has.PZN]<- NA
full_r1<- arrange(full_r1, episode.ID, TG_DateNum_antibiotic)
episode.duplicate<- duplicated(full_r1$episode.ID)
full_r1<- full_r1[!episode.duplicate,]
full_r1$time_until_antibiotic<- full_r1$TG_DateNum_antibiotic - 
  full_r1$start_date

full_r2<- left_join(full_r2, pzn.up, by = "uniPatID")
has.PZN<- full_r2$start_date <= full_r2$TG_DateNum_antibiotic & 
  full_r2$end_date >= full_r2$TG_DateNum_antibiotic
full_r2$TG_DateNum_antibiotic[!has.PZN]<- NA
full_r2<- arrange(full_r2, episode.ID, TG_DateNum_antibiotic)
episode.duplicate<- duplicated(full_r2$episode.ID)
full_r2<- full_r2[!episode.duplicate,]
full_r2$time_until_antibiotic<- full_r2$TG_DateNum_antibiotic - 
  full_r2$start_date
```

```{r}
# 9 extract summary statistics
summary.stats<- function(episodedf){
  no.patients<- length(levels(as.factor(episodedf$uniPatID)))
  no.episodes<- nrow(episodedf)
  age<- episodedf$age
  length.of.episode<- episodedf$length_of_episode
  
  numbers<- list(
    no.episodes= nrow(episodedf),
    no.patients= length(levels(as.factor(episodedf$uniPatID))),
    no.stammdata.there= sum(episodedf$stamm.is.there, na.rm = TRUE),
    earliest.recorded.episode.start= min(episodedf$start_date)|>
      TG_DateNum2date()|>
      as.character(),
    latest.recorded.episode.start= max(episodedf$start_date)|>
      TG_DateNum2date()|>
      as.character(),
    no.males=sum(episodedf$Maennl, na.rm = TRUE),
    no.females=sum(episodedf$Weibl, na.rm = TRUE),
    no.transgender=sum(episodedf$Transgen, na.rm = TRUE),
    no.undefined.sex=sum(episodedf$Geschlechtundef, na.rm = TRUE),
    
    percentage.chronically.diseased.patients= mean(as.character(levels(as.factor(episodedf$uniPatID))) %in% chronic.patients$chronic.patients),
    percentage.episodes.of.chronically.diseased= mean(episodedf$uniPatID %in% chronic.patients$chronic.patients),
    percentage.copd.patients= mean(as.character(levels(as.factor(episodedf$uniPatID))) %in% copd.vec),
    percentage.episodes.of.copd.patients= mean(episodedf$uniPatID %in% copd.vec),
    min.age= min(age, na.rm = TRUE),
    mean.age= mean(age, na.rm= TRUE),
    median.age= median(age, na.rm = TRUE),
    max.age= max(age, na.rm = TRUE),
    percentage.episodes.minors= mean(age<18, na.rm=TRUE),
    percentage.patients.minors= mean((age<18)[!duplicated(episodedf$uniPatID)], na.rm=TRUE),
    min.length.of.episode= min(length.of.episode),
    mean.length.of.episode= mean(length.of.episode),
    max.length.of.episode= max(length.of.episode),
    
    average.no.visit.per.patient=nrow(episodedf)/no.patients,
    percentage.stammdata.there= sum(episodedf$stamm_is_there, na.rm = TRUE)/no.episodes,
    percentage.males.episodes=mean(episodedf$Maennl, na.rm = TRUE),
    percentage.females.episodes=mean(episodedf$Weibl, na.rm = TRUE),
    percentage.males.patients=mean(episodedf$Maennl[!duplicated(episodedf$uniPatID)], na.rm = TRUE),
    percentage.females.patients=mean(episodedf$Weibl[!duplicated(episodedf$uniPatID)], na.rm = TRUE),
    no.private.insurance= sum(episodedf$PKV, na.rm= TRUE),
    percentage.private.insurance= mean(episodedf$PKV, na.rm= TRUE),
    percentage.retired.patients= mean(episodedf$Status_R[!duplicated(episodedf$uniPatID)], na.rm= TRUE),
    percentage.retired.episodes= mean(episodedf$Status_R, na.rm= TRUE),
    no.AUBs = sum(!is.na(episodedf$time_until_AUB)),
    percentage.AUBs.episodes = mean(!is.na(episodedf$time_until_AUB))
  )
  return(numbers)
}

t1_r1<- summary.stats(episodedf = full_r1)|>
  unlist()|>
  as.data.frame()
colnames(t1_r1)<- NULL
t1_r2<- summary.stats(episodedf = full_r2)|>
  unlist()|>
  as.data.frame()
colnames(t1_r2)<- NULL
write.table(t1_r1, "table1_r1.csv", sep = "; ")
write.table(t1_r2, "table1_r2.csv", sep = "; ")
```

```{r}
# create plots

# no. 32

```

```{r}
diag.parameters<- list(initial.or.last= "initial",type= 1)
discovery.tool(1, dependent.variable = "diag", research.question = "Welche Diagnosen wurden zuerst gestellt, R1")
discovery.tool(2, dependent.variable = "diag", research.question = "Welche Diagnosen wurden zuerst gestellt, R2")
discovery.tool(1, dependent.variable = "diag", selected.years = c(2000,2019), research.question = "Welche Diagnosen wurden zuerst gestellt, 2000-2019, R1")
discovery.tool(2, dependent.variable = "diag", selected.years = c(2000,2019), research.question = "Welche Diagnosen wurden zuerst gestellt, 2000-2019, R2")
discovery.tool(1, dependent.variable = "diag", pandemic = FALSE, research.question = "Welche Diagnosen wurden zuerst gestellt, ohne Pandemie R1")
discovery.tool(2, dependent.variable = "diag", pandemic = FALSE, research.question = "Welche Diagnosen wurden zuerst gestellt, ohne Pandemie, R2")

diag.parameters<- list(type= 2)
discovery.tool(1, dependent.variable = "diag", research.question = "An wie vielen Besuchen wurden Diagnosen gestellt, R1")
discovery.tool(2, dependent.variable = "diag", research.question = "An wie vielen Besuchen wurden Diagnosen gestellt, R2")

discovery.tool(1, dependent.variable = "age", agelims = c(1,90), research.question = "Wie alt waren die Patienten, R1")
discovery.tool(2, dependent.variable = "age", agelims = c(1,90), research.question = "Wie alt waren die Patienten, R2")
discovery.tool(1, dependent.variable = "age", agelims = c(18,90), research.question = "Wie alt waren die Patienten (ohne Minderjährige), R1")
discovery.tool(2, dependent.variable = "age", agelims = c(18,90), research.question = "Wie alt waren die Patienten (ohne Minderjährige), R2")

escalation.parameters_ueberweis<- list(type="1")
discovery.tool(2,dependent.variable = "escalation_ueberweis",research.question = "Wann wurden Patienten zu einem Spezialisten geschickt, R2")
escalation.parameters_ueberweis<- list(type="2")
discovery.tool(2,dependent.variable = "escalation_ueberweis",research.question = "Wann wurden Patienten zu einem Pneumologen geschickt, R2")
escalation.parameters_ueberweis<- list(type="3")
discovery.tool(2,dependent.variable = "escalation_ueberweis",research.question = "Wann wurden Patienten zu einem Radiologen geschickt, R2")
escalation.parameters_ueberweis<- list(type="4")
discovery.tool(2,dependent.variable = "escalation_ueberweis",research.question = "Wann wurden Patienten ins Krankenhaus geschickt, R2")

escalation.parameters_ueberweis<- list(type="1")
discovery.tool(1,dependent.variable = "escalation_ueberweis",research.question = "Wann wurden Patienten zu einem Spezialisten geschickt, R1")
escalation.parameters_ueberweis<- list(type="2")
discovery.tool(1,dependent.variable = "escalation_ueberweis",research.question = "Wann wurden Patienten zu einem Pneumologen geschickt, R1")
escalation.parameters_ueberweis<- list(type="3")
discovery.tool(1,dependent.variable = "escalation_ueberweis",research.question = "Wann wurden Patienten zu einem Radiologen geschickt, R1")
escalation.parameters_ueberweis<- list(type="4")
discovery.tool(1,dependent.variable = "escalation_ueberweis",research.question = "Wann wurden Patienten ins Krankenhaus geschickt, R1")
```

```{r}
diag.parameters<- list(initial.or.last= "initial",type= 1)
discovery.tool(1, dependent.variable = "diag", AUB=TRUE, research.question = "Welche Diagnosen wurden zuerst gestellt in AUB-Fällen, R1")
discovery.tool(2, dependent.variable = "diag", AUB=TRUE, research.question = "Welche Diagnosen wurden zuerst gestellt in AUB-Fällen, R2")
discovery.tool(1, dependent.variable = "diag", AUB=FALSE, research.question = "Welche Diagnosen wurden zuerst gestellt in nicht-AUB-Fällen, R1")
discovery.tool(2, dependent.variable = "diag", AUB=FALSE, research.question = "Welche Diagnosen wurden zuerst gestellt in nicht-AUB-Fällen, R2")
discovery.tool(1, dependent.variable = "diag", quarter.selection = 1, research.question = "Welche Diagnosen wurden zuerst gestellt in Q1, R1")
discovery.tool(2, dependent.variable = "diag", quarter.selection = 1, research.question = "Welche Diagnosen wurden zuerst gestellt in Q1, R2")
discovery.tool(1, dependent.variable = "diag", quarter.selection = 2, research.question = "Welche Diagnosen wurden zuerst gestellt in Q2, R1")
discovery.tool(2, dependent.variable = "diag", quarter.selection = 2, research.question = "Welche Diagnosen wurden zuerst gestellt in Q2, R2")
discovery.tool(1, dependent.variable = "diag", quarter.selection = 3, research.question = "Welche Diagnosen wurden zuerst gestellt in Q3, R1")
discovery.tool(2, dependent.variable = "diag", quarter.selection = 3, research.question = "Welche Diagnosen wurden zuerst gestellt in Q3, R2")
discovery.tool(1, dependent.variable = "diag", quarter.selection = 4, research.question = "Welche Diagnosen wurden zuerst gestellt in Q4, R1")
discovery.tool(2, dependent.variable = "diag", quarter.selection = 4, research.question = "Welche Diagnosen wurden zuerst gestellt in Q4, R2")
```
```{r}
#escalation lab plots
escalation.parameters_lab<- list(type=1)
discovery.tool(1,dependent.variable = "escalation_lab", research.question = "Wann wurde (irgend-) ein Labortest angeordnet, R1")
discovery.tool(2,dependent.variable = "escalation_lab", research.question = "Wann wurde (irgend-) ein Labortest angeordnet, R2")
escalation.parameters_lab<- list(type=4)
discovery.tool(1,dependent.variable = "escalation_lab", research.question = "Wann wurde auf C-reaktives Protein getestet, R1")
discovery.tool(2,dependent.variable = "escalation_lab", research.question = "Wann wurde auf C-reaktives Protein getestet, R2")
escalation.parameters_lab<- list(type=6)
discovery.tool(1,dependent.variable = "escalation_lab", research.question = "Wann wurden Leukozyten gemessen, R1")
discovery.tool(2,dependent.variable = "escalation_lab", research.question = "Wann wurden Leukozyten gemessen, R2")
escalation.parameters_lab<- list(type=7)
discovery.tool(1,dependent.variable = "escalation_lab", research.question = "Wann wurde auf Procalcitonin getestet, R1")
discovery.tool(2,dependent.variable = "escalation_lab", research.question = "Wann wurde auf Procalcitonin getestet, R2")
```

```{r}
#probably necessary to adjust the function
discovery.tool(1, dependent.variable = "age", agelims = c(18,150), research.question = "Wie alt waren die Patienten, ohne Minderjährige, R1")
discovery.tool(2, dependent.variable = "age", agelims = c(18,150), research.question = "Wie alt waren die Patienten, ohne Minderjährige, R2")
discovery.tool(1, dependent.variable = "escalation_antibiotics", research.question = "Wann wurden Antibiotika verschrieben, R1")
discovery.tool(2, dependent.variable = "escalation_antibiotics", research.question = "Wann wurden Antibiotika verschrieben, R2")
```
