---
title: "Cough Project Main File"
author: "Raphael Kroes"
date: "2023-12-07"
output: html_document
---

Procedure:

```{r}
# 1 Clear work space & load packages
library(readxl)
library(dplyr)
library(parallel)
library(lubridate)
library(ggplot2)
library(writexl)
```

```{r}
# 2
# Read in data
real.data<- TRUE
if(real.data){
  setwd("N:/StudentischeHilfskraefte/_Kroes (Christoph)/Routinedaten/01_Husten/R/DBnew")
names.vec<- c("Diag","ICPC","Labor","Stamm","Ueberweis")

# for (i in seq(1,length(names.vec))) {
#   file.name<- paste0("DB_",names.vec[i],"1_v01",".csv")
# 
#   im.file<- read.csv(file = file.name, header = TRUE, sep = ";")
# 
#   assign(names.vec[i],im.file)
# 
# }
# remove duplicate file and unnecessary name
# rm(file.name,im.file)

# Read in supplementary data
ListeKrankenkassen<- read.csv("https://github.com/rapkroes/Code_UKSH_Husten/blob/e67735f206a45437803f01e3fe0b6cacb84d3298/ListeKrankenkassen.csv")
altersstruktur_deutschland <- read.csv("https://github.com/rapkroes/Code_UKSH_Husten/blob/e67735f206a45437803f01e3fe0b6cacb84d3298/altersstruktur%20deutschland.csv")
colnames(altersstruktur_deutschland)<- c("altersjahre","bevoelkerungsstand")
icd10_blocks <- read.csv("https://github.com/rapkroes/Code_UKSH_Husten/blob/bb08bfe63a3a69ff1a2d7fdadf2c6e0dfc9d3785/icd10_blocks.csv")
icd10_description<- read_excel("icd10_description.xlsx")
selected.lab.descriptions<- read_excel("freitextanalyse.xlsx")

# read in functions
source("//fileserver1.uni-luebeck.de/ifa_homes/raphaelkroes/Documents/GitHub/Code_UKSH_Husten/functions.R")

}else{
  source("fakedgp_work.R")
}
```

```{r}
# 3
# The patient with unipatID 2 (PatID=1 and index=1) has two dates of birth and shows the hallmarks of a test patient (e.g. for testing new computer equipment). Whatever the reason for the two different dates, we remove them from further data analysis.

diag.up<- Diag3 |> 
  select(uniPatID,TG_DateNum,DiagTyp,icd10)|>
  distinct()
diag.up<- diag.up[diag.up$uniPatID!=2,]
diag.up$chronic<- as.character(diag.up$DiagTyp)

#add variable for chronic disease
diag.up$chronic[diag.up$chronic=="DD"]<- 1
diag.up$chronic[diag.up$chronic!="1"]<- 0
diag.up$chronic<- as.numeric(diag.up$chronic)
diag.up$chronic[is.na(diag.up$chronic)]<- 0

#find patients with Chronic Pulmonary Obstructive Disease (COPD)
copd.vec<- as.character(levels(as.factor(diag.up$uniPatID[grepl("J44",diag.up$icd10)])))

# find all other chronically diseased people
im<- diag.up|>
  select(uniPatID,DiagTyp,icd10)|>
  distinct()
chronic.patients<- im$uniPatID[im$DiagTyp=="DD"]
chronic.patients<- as.data.frame(table(chronic.patients))
rm(im)

ipc.up<- IPC23 |>
  select(uniPatID,TG_DateNum,AnamnTyp,ipc2)
ipc.up<- ipc.up[ipc.up$uniPatID!=2,]

labor.up<- Labor3
labor.up$labtest<- 1
labor.up<- labor.up|>
  select(uniPatID,TG_DateNum,Untersuchung,Unterstext,labtest)|>
  distinct()
detail.mat<- matrix(NA,ncol=6,nrow=nrow(labor.up))
for(i in 1:6){
  text.vec<- selected.lab.descriptions$text_description[selected.lab.descriptions[,2+i]==1]
  text.vec<- text.vec[!is.na(text.vec)]
  detail.mat[,i]<- as.numeric(labor.up$Unterstext %in% text.vec)
}
detail.mat<- as.data.frame(detail.mat)
colnames(detail.mat)<- colnames(selected.lab.descriptions)[-c(1,2)]
labor.up<- cbind(labor.up,detail.mat)
labor.up<- labor.up[labor.up$uniPatID!=2,]

stamm.up<- Stamm3
stamm.up$PKV<- IK2PKV(stamm.up$IK)
stamm.up<- stamm.up|> 
  select(-PatID,-index_i,-IK,-Kasse,-PLZ)|>
  distinct()|>
  arrange(uniPatID,desc(TG_DateNum))
stamm.up<- stamm.up[stamm.up$uniPatID!=2,]

ueberweis.up<- Ueberweis3|>
  select(uniPatID,TG_DateNum,Uberw_Pneumo,Uberw_Radiol,Uberw_KH) |>
  filter(Uberw_Pneumo>0|Uberw_Radiol>0|Uberw_KH>0)|>
  distinct()
ueberweis.up<- ueberweis.up[ueberweis.up$uniPatID!=2,]
```


```{r}
# 4 free up memory by clearing the original, raw datasets out
rm(list = names.vec)
```

```{r}
# 5
contains.multiple.entries(diag.up)
contains.multiple.entries(ipc.up)
contains.multiple.entries(labor.up)
contains.multiple.entries(stamm.up)
contains.multiple.entries(ueberweis.up)

```

STOP: Every patient/date combination must be unique. The difference between number of rows and patient/ time combinations must therefore be 0. This is what contains.multiple.entries checks for. We believe diag.up, ipc.up, and pzn.up have multiple entries for the same date by design. We believe stamm.up, impf.up, labor.up, and ueberweis.up should have only one line per patient/ time combination. In #6.1 we remedy the presumed errors by selecting the last entry for each patient/ time combination. In #6.2 we write the multiple data points of diag.up, ipc.up, and pzn.up in additional columns. Both procedures leave us with unique date/ time combinations for each data set.
In #6.2, we do not keep all entries for diag.up and ipc.up. There are a few entries with unreasonably high numbers of diagnoses or symptoms. Therefore, we truncate the number observations at the 95% quantile of the distribution of entries per combination. If the last sentence is not clear in meaning, please run the commented code in chunk #6.2 to gain better insight.

```{r}
# 5.1

labor.up<- data.repair.new(labor.up)
contains.multiple.entries(labor.up)

stamm.up<- data.repair.new(stamm.up)
contains.multiple.entries(stamm.up)

ueberweis.up<- data.repair.new(ueberweis.up)
contains.multiple.entries(ueberweis.up)

```

```{r}
# 5.2
x_diag<- quantile(table(paste(diag.up$uniPatID,diag.up$TG_DateNum)), probs= 0.95)
#x_ipc<- quantile(table(paste(ipc.up$uniPatID,ipc.up$TG_DateNum)), probs= 0.95)

# table(paste0(diag.up$uniPatID,diag.up$TG_DateNum)
# quantile(table(paste0(diag.up$uniPatID,diag.up$TG_DateNum)))

diag.up_2<- aligner.parallel.new(diag.up, x_diag,100,4)
contains.multiple.entries(diag.up_2)

# ipc.up_2<- aligner.parallel.new(ipc.up, x_ipc,100,4)
# contains.multiple.entries(ipc.up_2)

```

```{r}
# 6 create episodes based on the data
#episodes<- episode.fun.new(ipc.up_2,56)
episodes<- episode.fun.alt(ipc.up, 21)
```

There must be no overlap in the timing of the episodes in order to map diagnoses and treatments to the episodes.
There is no decision rule we can enforce that distinguishes perfectly whether episodes match or match not. Therefore, we implement different decision rules.

```{r}
# 7 create non-overlapping episodes

#decision rule 1: If the timing of episodes overlaps, we treat them as one episode
#decision rule 2: If the timing of episodes overlaps, we treat them as two distinct episodes. The last day of the earlier episode is the day before the new episode begins.

episodes_r1<- episodes.dr1(episodes)
episodes_r2<- episodes.dr2(episodes)

# test for how many overlaps there are
sum(episodes.overlap.finder(episodes_r1)$overlap)
sum(episodes.overlap.finder(episodes_r2)$overlap)
```

```{r}
#create complete datasets
episodes.stamm_r1<- add.stamm.new.par(episodes_r1,stamm.up,50,2)
episodes.diag_r1<- add.diag.par(episodes_r1,diag.up_2,50,2)
episodes.labor_r1<- add.lab.par(episodes_r1,labor.up,50,2)
episodes.ueberweis_1<- add.ueberweis.par(episodes_r1,ueberweis.up,50,2)
full_r1<- cbind(arrange(episodes.stamm_r1,uniPatID,start_date),
                arrange(episodes.diag_r1,uniPatID,start_date),
                arrange(episodes.labor_r1,uniPatID,start_date),
                arrange(episodes.ueberweis_1,uniPatID,start_date))

#remove duplicate columns
full_r1<- full_r1[,!duplicated(colnames(full_r1))]

#same procedure for decision rule 2
episodes.stamm_r2<- add.stamm.new.par(episodes_r2,stamm.up,50,2)
episodes.diag_r2<- add.diag.par(episodes_r2,diag.up_2,50,2)
episodes.labor_r2<- add.lab.par(episodes_r2,labor.up,50,2)
episodes.ueberweis_2<- add.ueberweis.par(episodes_r2,ueberweis.up,50,2)
full_r2<- cbind(arrange(episodes.stamm_r2,uniPatID,start_date),
                arrange(episodes.diag_r2,uniPatID,start_date),
                arrange(episodes.labor_r2,uniPatID,start_date),
                arrange(episodes.ueberweis_2,uniPatID,start_date))

full_r2<- full_r2[,!duplicated(colnames(full_r2))]

#no.chronic diseases 
for(k in 1:2){
  im<- get(paste0("full_r",k))
  no.chronic.diseases<- numeric(nrow(im))
  for(i in seq(1,nrow(im))){
    pat<- im$uniPatID[i]
    loc<- which(chronic.patients$chronic.patients==pat)
    if(length(loc)==1){
      no.chronic.diseases[i]<- chronic.patients$Freq[loc]
    }else if(length(loc)>1){
      stop("several entries found for the same patient!")
    }
    
  }
  names.vec<- c(colnames(im),"no.chronic.diseases")
  im<- cbind(im,no.chronic.diseases)
  colnames(im)<- names.vec
  
  assign(paste0("full_r",k),im)
  rm(im)
}


for(k in 1:2){
  im<- get(paste0("full_r",k))
  
  #find cases where at least one initial diagnosis was preliminary
  first.cols<- grep("first_icd10",colnames(im))
  last.cols<- grep("last_icd10",colnames(im))
  
  im_first<- apply(im[,first.cols],2,FUN = function(dv){
    im_dv<- substr(dv,nchar(dv),nchar(dv))
    return(grepl("V",im_dv))
  })
  im_last<- apply(im[,last.cols],2,FUN = function(dv){
    im_dv<- substr(dv,nchar(dv),nchar(dv))
    return(grepl("V",im_dv))
  })
  
  im$first_diag_V_present<- rowSums(im_first)>0
  im$last_diag_V_present<- rowSums(im_last)>0
  
  
  #find cases where an AUB was issued on the first visit
  AUB.cols<- grepl("first_DiagTyp",colnames(im))
  im_2<- apply(im[,AUB.cols],2,FUN = function(dv){grepl("AUB",dv)})
  im$AUB_issued<- rowSums(im_2)>0
  
  #add start month/ quarter
  im$start_month<- month(TG_DateNum2date(im$start_date))
  im$start_quarter<- quarter(TG_DateNum2date(im$start_date))
  ###
  assign(paste0("full_r",k),im)
  rm(im)
}


```

```{r}
# 9 extract summary statistics
summary.stats<- function(episodedf){
  no.patients<- length(levels(as.factor(episodedf$uniPatID)))
  no.episodes<- nrow(episodedf)
  age<- year(TG_DateNum2date(episodedf$start_date)) - episodedf$Geburtsjahr
  length.of.episode<- episodedf$end_date-episodedf$start_date
  
  numbers<- list(
    no.episodes= nrow(episodedf),
    no.patients= length(levels(as.factor(episodedf$uniPatID))),
    no.stammdata.there= sum(episodedf$stamm.is.there, na.rm = TRUE),
    earliest.recorded.episode.start= TG_DateNum2date(min(episodedf$start_date)),
    latest.recorded.episode.start= TG_DateNum2date(max(episodedf$start_date)),
    no.males=sum(episodedf$Maennl, na.rm = TRUE),
    no.females=sum(episodedf$Weibl, na.rm = TRUE),
    no.transgender=sum(episodedf$Transgen, na.rm = TRUE),
    no.undefined.sex=sum(episodedf$Geschlechtundef, na.rm = TRUE),
    
    percentage.chronically.diseased.patients= mean(as.character(levels(as.factor(episodedf$uniPatID))) %in% chronic.patients$chronic.patients),
    percentage.episodes.of.chronically.diseased= mean(episodedf$uniPatID %in% chronic.patients$chronic.patients),
    percentage.copd.patients= mean(as.character(levels(as.factor(episodedf$uniPatID))) %in% copd.vec),
    percentage.episodes.of.copd.patients= mean(episodedf$uniPatID %in% copd.vec),
    min.age= min(age, na.rm = TRUE),
    mean.age= mean(age, na.rm= TRUE),
    median.age= median(age, na.rm = TRUE),
    max.age= max(age, na.rm = TRUE),
    percentage.episodes.minors= mean(age<18, na.rm=TRUE),
    percentage.patients.minors= mean((age<18)[!duplicated(episodedf$uniPatID)], na.rm=TRUE),
    min.length.of.episode= min(length.of.episode),
    mean.length.of.episode= mean(length.of.episode),
    max.length.of.episode= max(length.of.episode),
    
    average.no.visit.per.patient=nrow(episodedf)/no.patients,
    percentage.stammdata.there= sum(episodedf$stamm_is_there, na.rm = TRUE)/no.episodes,
    percentage.males.episodes=mean(episodedf$Maennl, na.rm = TRUE),
    percentage.females.episodes=mean(episodedf$Weibl, na.rm = TRUE),
    percentage.males.patients=mean(episodedf$Maennl[!duplicated(episodedf$uniPatID)], na.rm = TRUE),
    percentage.females.patients=mean(episodedf$Weibl[!duplicated(episodedf$uniPatID)], na.rm = TRUE),
    no.private.insurance= sum(episodedf$PKV, na.rm= TRUE),
    percentage.private.insurance= mean(episodedf$PKV, na.rm= TRUE),
    percentage.retired.patients= mean(episodedf$Status_R[!duplicated(episodedf$uniPatID)], na.rm= TRUE),
    percentage.retired.episodes= mean(episodedf$Status_R, na.rm= TRUE)
  )
  return(numbers)
}

summary.stats(episodedf = full_r1)
summary.stats(episodedf = full_r2)

```

```{r}
# create plots

# no. 32
discovery.tool<- function(decision.rule, agelims=c(1,150), insurance=c("all","GKV","PKV")[1], remove.copd=FALSE, lims.chronic.diseases=c(0,100), pandemic="none", preliminary.diag=c(NA,TRUE,FALSE)[1], AUB=c(NA,TRUE,FALSE)[1], quarter.selection=1:4, month.selection=1:12, dependent.variable, research.question){
  # Tool to create plots and tables for specific data requests.
  # decision.rule is an integer between 1 and 5 giving the decision rule for how to deal with overlaps in the data set. Can currently only be set to 1 or 2.
  # insurance can be selected as "GKV" or "PKV" in order to restrict the patients to being insured by a public/ private insurer
  # remove.copd can be set to TRUE to remove all patients that were registered with COPD within the time of the data
  # lims.chronic.diseases is a two element vector with the lowest and highest numbers of chronic diseases that are to be considered. By default, patients with 0 to 100 different chronic diseases are considered. Example: only patients with three chronic diseases are to be considered-> set lims.chronic.diseases=c(3,3); only people with two or fewer chronic diseases are to be considered-> set lims.chronic.diseases=c(0,2). Note that the people for which no data is recorded are kept by default in the analysis.
  # pandemic: if specified, set it to TRUE if only pandemic data is to be analysed, and to false if only data before the pandemic is to be included.
  # dependent.variable specifies the dependent variable to be looked at. Current options are: diag, age, escalation_lab, escalation_ueberweis.
  # constraint.list is a list of constraints what cases are to be selected.
  # research.question is the question that the plot/ table aims to answer. It is used as label for the plot and is used to name the generated files. Therefore, it must not contain any kind of punctuation (only underline permitted)! The function adds a question mark automatically at the end of each label with the research question!
  #browser()
    
  # 1. setup of parameters and data
  if(decision.rule==1){
    episodedf<- full_r1
  }else if(decision.rule==2){
    episodedf<- full_r2
  }else if(decision.rule==3){
    episodedf<- full_r3
  }else if(decision.rule==4){
    episodedf<- full_r4
  }else if(decision.rule==5){
    episodedf<- full_r5
  }else{
    stop("The decision rule must be an integer between 1 and 5!")
  }
  
  #age
  age.vec<- as.numeric(year(TG_DateNum2date(episodedf$start_date)))-episodedf$Geburtsjahr
  age.selector<- agelims[1]<= age.vec & agelims[2]>= age.vec
  age.selector[is.na(age.selector)]<- TRUE
  episodedf<- episodedf[age.selector,]
  
  #insurance
  if(insurance=="PKV"){
    episodedf<- episodedf[episodedf$PKV==1,]
  }else if(insurance=="GKV"){
    episodedf<- episodedf[episodedf$PKV==0,]
  }
  
  #copd
  if(remove.copd){
    keep.vec<- numeric(nrow(episodedf))
    for(i in seq(1,nrow(episodedf))){
      if(episodedf$uniPatID[i] %in% copd.vec){
        keep.vec[i]<- FALSE
      }else{
        keep.vec[i]<- TRUE
      }
    }
    episodedf<- episodedf[keep.vec,]
  }
  
  #number of chronic diseases
  selector<- episodedf$no.chronic.diseases>= lims.chronic.diseases[1] & episodedf$no.chronic.diseases<=lims.chronic.diseases[2]
  selector[is.na(selector)]<- TRUE
  episodedf<- episodedf[selector,]
  
  earliest.TG_Date<- min(episodedf$start_date)
  latest.TG_Date<- max(episodedf$start_date)
  earliest.year.POSIXlt<- year(TG_DateNum2date(earliest.TG_Date))
  latest.year.POSIXlt<- year(TG_DateNum2date(latest.TG_Date))
  no.years<- latest.year.POSIXlt-earliest.year.POSIXlt
  pandemic.start<- date2TG_DateNum("2020-01-01")
  pandemic.end<- date2TG_DateNum("2023-01-01")
  length.pandemic<- 3
  
  if(pandemic==TRUE){
    episodedf<- episodedf[episodedf$start_date>=pandemic.start & episodedf$start_date<pandemic.end,]
  }else if(pandemic==FALSE){
    episodedf<- episodedf[episodedf$start_date<pandemic.start,]
  }else if(pandemic=="none"){
    #nothing happens
  }else{
    stop("pandemic must be specified as TRUE, FALSE, or be non-specified.")
  }
  
  if(!is.na(preliminary.diag)){
      if(preliminary.diag==TRUE){
      episodedf<- episodedf[episodedf$first_diag_V_present,]
    }else if(preliminary.diag==FALSE){
      episodedf<- episodedf[!episodedf$first_diag_V_present,]
    }
  }
  
  if(nrow(episodedf)==0){
    stop("Due to the parameter configuration there are no episodes left after accounting for preliminary.diag")
  }
  
  if(!is.na(AUB)){
      if(AUB==TRUE){
      episodedf<- episodedf[episodedf$AUB_issued,]
    }else if(AUB==FALSE){
      episodedf<- episodedf[!episodedf$AUB_issued,]
    }
  }
  
  if(nrow(episodedf)==0){
    stop("Due to the parameter configuration there are no episodes left after accounting for AUB")
  }
  
  episodedf<- episodedf|>
    filter(start_quarter %in% quarter.selection)|>
    filter(start_month %in% month.selection)
  
  if(nrow(episodedf)==0){
    stop("Due to the parameter configuration there are no episodes left after accounting for quarter.selection and month.selection")
  }
  
  #creating plots and tables
  
  #####diag#####diag#####diag#####diag#####diag#####diag#####diag#####diag#####diag#####diag#####diag#####diag#####diag#####diag#####diag#####diag#####diag#####diag#####diag#####diag
  if(dependent.variable=="diag"){
    if(diag.parameters[["type"]]==1){
      if(diag.parameters[["initial.or.last"]]=="last"){
        all.diagnoses<- as.vector(as.matrix(episodedf[,grepl("last_icd10", colnames(episodedf))]))
      }else if(diag.parameters[["initial.or.last"]]=="initial"){
        all.diagnoses<- as.vector(as.matrix(episodedf[,grepl("first_icd10", colnames(episodedf))]))
      }else{
        stop("initial.or.last in diag.parameters is incorrectly specified")
      }
      
      all.diagnoses<- all.diagnoses[!is.na(all.diagnoses)]
      all.diagnoses<- all.diagnoses[all.diagnoses!="0"]
        
      chapters<- icd10.to.chapter(all.diagnoses)[,2]
      im<- table(chapters)
      chapter.no<- as.numeric(names(im))
      names(im)<- NULL
      prob<- numeric(22)
      prob[chapter.no]<- im
      prob<- prob/sum(prob)
      d.chapter<- data.frame(x=1:22,prob=prob)
      
      
      blocks<- icd10.to.block(all.diagnoses)
      im<- table(blocks[,1])
      blocks.no<- as.numeric(names(im))
      names(im)<- NULL
      prob<- numeric(241)
      prob[blocks.no]<- im
      prob<- prob/sum(prob)
      d.block_num<- data.frame(x=1:241,prob=prob)
      d.block_description<- data.frame(x=icd10_blocks$description, prob=prob)
      
      three.St<- icd10.to.3St(all.diagnoses)
      d.3St<- as.data.frame(table(paste0(three.St$codes,"- ",three.St$description)))
      colnames(d.3St)<- c("description","frequency")
      d.3St$icd10code<- as.data.frame(table(three.St$codes))
      d.3St$prob<- d.3St$frequency/sum(d.3St$frequency)
      
      p<- ggplot(d.chapter, aes(x=x, y=prob)) +
        geom_bar(stat = "identity", fill="skyblue") +
        ylim(0,0.6) +
        scale_y_continuous(labels = scales::percent_format(), limits = c(0,0.6)) +
        labs(title = paste0(research.question,"?"),x = "ICD10 chapter", y= "percentage")
      ggsave(paste0(research.question,"_chapter.png"), plot = p, path = getwd(), device = "png")
      
      p<- ggplot(d.block_num, aes(x=x, y=prob)) +
        geom_bar(stat = "identity", fill="skyblue") +
        ylim(0,0.5) +
        scale_y_continuous(labels = scales::percent_format(), limits = c(0,0.6)) +
        labs(title = paste0(research.question,"?"),x = "ICD10 block", y= "percentage")
      ggsave(paste0(research.question,"_block_num.png"), plot = p, path = getwd(), device = "png")
      
      p<- ggplot(d.block_description, aes(x=x, y=prob)) +
        geom_bar(stat = "identity", fill="skyblue") +
        ylim(0,0.5) +
        scale_y_continuous(labels = scales::percent_format(), limits = c(0,0.6)) +
        labs(title = paste0(research.question,"?"),x = "ICD10 block", y= "percentage")
      ggsave(paste0(research.question,"_block_description.png"), plot = p, path = getwd(), device = "png")
      
      write_xlsx(data.frame(no=1:241,description=icd10_blocks$description, probability=prob),paste0(research.question,".xlsx"))
      
      write_xlsx(d.3St, paste0("icd10_3St_",research.question,".xlsx"))
    
    #distribution of number of diagnoses
    }else if(diag.parameters[["type"]]==2){
      x<- episodedf$no.matches_diag
      x<- x[!is.na(x)]
      
      im<- table(x)
      allocation<- as.numeric(names(im))
      names(im)<- NULL
      prob<- numeric(max(allocation)+1)
      prob[allocation+1]<- im
      prob<- prob/sum(prob)
      distr.df<- data.frame(no.diagnoses=seq(0,max(allocation)),no.occurrences=prob)
      
      p<- ggplot(distr.df,aes(x=no.diagnoses, y=no.occurrences)) +
        geom_bar(stat = "identity", fill="skyblue") +
        scale_y_continuous(labels = scales::percent_format()) +
        labs(title = paste0(research.question,"?"),x = "number of occurrences", y= "percentage")
      ggsave(paste0(research.question,"_distr_matches.png"), plot = p, path = getwd(), device = "png")
    }
    
    
    #####age#####age#####age#####age#####age#####age#####age#####age#####age#####age#####age#####age#####age#####age#####age#####age#####age#####age#####age#####age#####age#####age#####age#####age
    
  }else if(dependent.variable=="age"){
    x<- as.numeric(year(TG_DateNum2date(episodedf$start_date)))-episodedf$Geburtsjahr
    if(sum(is.na(x))>0){
      warning(paste("There are",sum(is.na(x)),"entries where no birth date is available. This corresponds to",round(sum(is.na(x))/length(x),2)*100), "% of all entries. The NA results are dropped in the following.")
      x<- x[!is.na(x)]
    }
    
    im<- table(x)
    ages<- as.numeric(names(im))
    names(im)<- NULL
    prob<- numeric(length = agelims[2])
    prob[ages]<- im
    if(agelims[1]>=2){
      prob<- prob[-seq(1,agelims[1]-1)]
    }
    prob<- prob/sum(prob)
    d<- data.frame(x=seq(agelims[1],agelims[2]),prob=prob)|>
      filter(x>=agelims[1])
    
    d$y<- age.weights(agelims[1],agelims[2])
    
    p<- ggplot(d, aes(x = x)) +
      geom_bar(aes(y = prob, fill = "Patient age"), stat = "identity") +
      geom_line(aes(y = y, color = "Age distribution of Germany")) +
      scale_y_continuous(labels = scales::percent_format()) +
      labs(title = paste0(research.question,"?"),
           x = "Age in years",
           y = "Percentage") +
      scale_fill_manual(values = c("skyblue"), labels = c("Patient age")) +
      scale_color_manual(values = c("red"), labels = c("Age distribution of Germany")) +
      theme(legend.position = "bottom")
    
    ggsave(paste0(research.question,".png"), plot = p, path = getwd(), device = "png")
    
    #####escalation_lab#####escalation_lab#####escalation_lab#####escalation_lab#####escalation_lab#####escalation_lab#####escalation_lab#####escalation_lab#####escalation_lab#####escalation_lab#####escalation_lab
    
  }else if(dependent.variable=="escalation_lab"){
    
    if(escalation.parameters_lab[["type"]]==1){
      #lab test, generally
      x<- episodedf$labtest-episodedf$start_date
      x<- x[!is.na(x)]
    }else if(escalation.parameters_lab[["type"]]==2){
      #normal blood
      x<- episodedf$blood_normal-episodedf$start_date
      x<- x[!is.na(x)]
    }else if(escalation.parameters_lab[["type"]]==3){
      #differential blood test
      x<- episodedf$blood_large_test-episodedf$start_date
      x<- x[!is.na(x)]
    }else if(escalation.parameters_lab[["type"]]==4){
      #CRP
      x<- episodedf$CRP-episodedf$start_date
      x<- x[!is.na(x)]
    }else if(escalation.parameters_lab[["type"]]==5){
      #erythocytes
      x<- episodedf$ery-episodedf$start_date
      x<- x[!is.na(x)]
    }else if(escalation.parameters_lab[["type"]]==6){
      #leucocytes
      x<- episodedf$leuko-episodedf$start_date
      x<- x[!is.na(x)]
    }else if(escalation.parameters_lab[["type"]]==7){
      #procalcitonin
      x<- episodedf$procalcitonin-episodedf$start_date
      x<- x[!is.na(x)]
    }
    
    im<- table(x)
    allocation<- as.numeric(names(im))
    names(im)<- NULL
    prob<- numeric(max(allocation)+1)
    prob[allocation+1]<- im
    prob<- prob/sum(prob)
    d<- data.frame(x=seq(0,max(allocation)),prob=prob)
    
    
    p<- ggplot(d, aes(x=x, y=prob)) +
      geom_bar(stat = "identity", fill="skyblue") +
      scale_y_continuous(labels = scales::percent_format()) +
      labs(title = paste0(research.question,"?"),
           x = "number of days since initial cough", 
           y= "percentage",
           subtitle = paste("based on", length(x), "episodes"))
    ggsave(paste0(research.question,".png"), plot = p, path = getwd(), device = "png")
    
    
    #####escalation_ueberweis#####escalation_ueberweis#####escalation_ueberweis#####escalation_ueberweis#####escalation_ueberweis#####escalation_ueberweis#####escalation_ueberweis#####escalation_ueberweis
    
    }else if(dependent.variable=="escalation_ueberweis"){
      if(escalation.parameters_ueberweis[["type"]]==1){
      #referral to specialist care
      x<- cbind(episodedf$Uberw_Pneumo-episodedf$start_date,episodedf$Uberw_Radiol-episodedf$start_date,episodedf$Uberw_KH-episodedf$start_date)
      x<- apply(x, 1, function(row) {
    if (all(is.na(row))) {
      return(NA)
    } else {
      return(min(row, na.rm = TRUE))
    }
  })
      x<- x[!is.na(x)]
      warning(paste("There were", length(x), "episodes when patients were referred to a specialist."))
    }else if(escalation.parameters_ueberweis[["type"]]==2){
      #referral pulmonologist
      x<- episodedf$Uberw_Pneumo-episodedf$start_date
      x<- x[!is.na(x)]
      warning(paste("There were", length(x), "episodes when patients were referred to a pulmonologist."))
    }else if(escalation.parameters_ueberweis[["type"]]==3){
      #referral radiologist
      x<- episodedf$Uberw_Radiol-episodedf$start_date
      x<- x[!is.na(x)]
      warning(paste("There were", length(x), "episodes when patients were referred to a radiologist."))
    }else if(escalation.parameters_ueberweis[["type"]]==4){
      #referral hospital
      x<- episodedf$Uberw_KH-episodedf$start_date
      x<- x[!is.na(x)]
      warning(paste("There were", length(x), "episodes when patients were referred to a hospital."))
    }
    
    im<- table(x)
    allocation<- as.numeric(names(im))
    names(im)<- NULL
    prob<- numeric(max(allocation)+1)
    prob[allocation+1]<- im
    prob<- prob/sum(prob)
    d<- data.frame(x=seq(0,max(allocation)),prob=prob)
    
    
    p<- ggplot(d, aes(x=x, y=prob)) +
      geom_bar(stat = "identity", fill="skyblue") +
      scale_y_continuous(labels = scales::percent_format()) +
      labs(title = paste0(research.question,"?"),
           x = "number of days since initial cough", 
           y= "percentage",
           subtitle = paste("based on", length(x), "episodes"))
    ggsave(paste0(research.question,".png"), plot = p, path = getwd(), device = "png")
  }
}
```

```{r}
diag.parameters<- list(initial.or.last= "initial",type= 1)
discovery.tool(1, dependent.variable = "diag", research.question = "Welche Diagnosen wurden zuerst gestellt, R1")
discovery.tool(2, dependent.variable = "diag", research.question = "Welche Diagnosen wurden zuerst gestellt, R2")
discovery.tool(1, dependent.variable = "diag", pandemic = FALSE, research.question = "Welche Diagnosen wurden zuerst gestellt, ohne Pandemie R1")
discovery.tool(2, dependent.variable = "diag", pandemic = FALSE, research.question = "Welche Diagnosen wurden zuerst gestellt, ohne Pandemie, R2")

diag.parameters<- list(type= 2)
discovery.tool(1, dependent.variable = "diag", research.question = "An wie vielen Besuchen wurden Diagnosen gestellt, R1")
discovery.tool(2, dependent.variable = "diag", research.question = "An wie vielen Besuchen wurden Diagnosen gestellt, R2")

discovery.tool(1, dependent.variable = "age", agelims = c(1,90), research.question = "Wie alt waren die Patienten, R1")
discovery.tool(2, dependent.variable = "age", agelims = c(1,90), research.question = "Wie alt waren die Patienten, R2")
discovery.tool(1, dependent.variable = "age", agelims = c(18,90), research.question = "Wie alt waren die Patienten (ohne Minderjährige), R1")
discovery.tool(2, dependent.variable = "age", agelims = c(18,90), research.question = "Wie alt waren die Patienten (ohne Minderjährige), R2")

escalation.parameters_ueberweis<- list(type="1")
discovery.tool(2,dependent.variable = "escalation_ueberweis",research.question = "Wann wurden Patienten zu einem Spezialisten geschickt, R2")
escalation.parameters_ueberweis<- list(type="2")
discovery.tool(2,dependent.variable = "escalation_ueberweis",research.question = "Wann wurden Patienten zu einem Pneumologen geschickt, R2")
escalation.parameters_ueberweis<- list(type="3")
discovery.tool(2,dependent.variable = "escalation_ueberweis",research.question = "Wann wurden Patienten zu einem Radiologen geschickt, R2")
escalation.parameters_ueberweis<- list(type="4")
discovery.tool(2,dependent.variable = "escalation_ueberweis",research.question = "Wann wurden Patienten ins Krankenhaus geschickt, R2")

escalation.parameters_ueberweis<- list(type="1")
discovery.tool(1,dependent.variable = "escalation_ueberweis",research.question = "Wann wurden Patienten zu einem Spezialisten geschickt, R1")
escalation.parameters_ueberweis<- list(type="2")
discovery.tool(1,dependent.variable = "escalation_ueberweis",research.question = "Wann wurden Patienten zu einem Pneumologen geschickt, R1")
escalation.parameters_ueberweis<- list(type="3")
discovery.tool(1,dependent.variable = "escalation_ueberweis",research.question = "Wann wurden Patienten zu einem Radiologen geschickt, R1")
escalation.parameters_ueberweis<- list(type="4")
discovery.tool(1,dependent.variable = "escalation_ueberweis",research.question = "Wann wurden Patienten ins Krankenhaus geschickt, R1")
```

```{r}
diag.parameters<- list(initial.or.last= "initial",type= 1)
discovery.tool(1, dependent.variable = "diag", AUB=TRUE, research.question = "Welche Diagnosen wurden zuerst gestellt in AUB-Fällen, R1")
discovery.tool(2, dependent.variable = "diag", AUB=TRUE, research.question = "Welche Diagnosen wurden zuerst gestellt in AUB-Fällen, R2")
discovery.tool(1, dependent.variable = "diag", AUB=FALSE, research.question = "Welche Diagnosen wurden zuerst gestellt in nicht-AUB-Fällen, R1")
discovery.tool(2, dependent.variable = "diag", AUB=FALSE, research.question = "Welche Diagnosen wurden zuerst gestellt in nicht-AUB-Fällen, R2")
discovery.tool(1, dependent.variable = "diag", quarter.selection = 1, research.question = "Welche Diagnosen wurden zuerst gestellt in Q1, R1")
discovery.tool(2, dependent.variable = "diag", quarter.selection = 1, research.question = "Welche Diagnosen wurden zuerst gestellt in Q1, R2")
discovery.tool(1, dependent.variable = "diag", quarter.selection = 2, research.question = "Welche Diagnosen wurden zuerst gestellt in Q2, R1")
discovery.tool(2, dependent.variable = "diag", quarter.selection = 2, research.question = "Welche Diagnosen wurden zuerst gestellt in Q2, R2")
discovery.tool(1, dependent.variable = "diag", quarter.selection = 3, research.question = "Welche Diagnosen wurden zuerst gestellt in Q3, R1")
discovery.tool(2, dependent.variable = "diag", quarter.selection = 3, research.question = "Welche Diagnosen wurden zuerst gestellt in Q3, R2")
discovery.tool(1, dependent.variable = "diag", quarter.selection = 4, research.question = "Welche Diagnosen wurden zuerst gestellt in Q4, R1")
discovery.tool(2, dependent.variable = "diag", quarter.selection = 4, research.question = "Welche Diagnosen wurden zuerst gestellt in Q4, R2")
```
```{r}
#escalation lab plots
escalation.parameters_lab<- list(type=1)
discovery.tool(1,dependent.variable = "escalation_lab", research.question = "Wann wurde (irgend-) ein Labortest angeordnet, R1")
discovery.tool(2,dependent.variable = "escalation_lab", research.question = "Wann wurde (irgend-) ein Labortest angeordnet, R2")
escalation.parameters_lab<- list(type=2)#######here
discovery.tool(1,dependent.variable = "escalation_lab", research.question = "Wann wurde ein Blutbild angeordnet, R1")
discovery.tool(2,dependent.variable = "escalation_lab", research.question = "Wann wurde ein Blutbild angeordnet, R2")
escalation.parameters_lab<- list(type=4)
discovery.tool(1,dependent.variable = "escalation_lab", research.question = "Wann wurde auf C-reaktives Protein getestet, R1")
discovery.tool(2,dependent.variable = "escalation_lab", research.question = "Wann wurde auf C-reaktives Protein getestet, R2")
escalation.parameters_lab<- list(type=6)
discovery.tool(1,dependent.variable = "escalation_lab", research.question = "Wann wurden Leukozyten gemessen, R1")
discovery.tool(2,dependent.variable = "escalation_lab", research.question = "Wann wurden Leukozyten gemessen, R2")
escalation.parameters_lab<- list(type=7)
discovery.tool(1,dependent.variable = "escalation_lab", research.question = "Wann wurde auf Procalcitonin getestet, R1")
discovery.tool(2,dependent.variable = "escalation_lab", research.question = "Wann wurde auf Procalcitonin getestet, R2")
```

```{r}
#probably necessary to adjust the function
discovery.tool(1, dependent.variable = "age", agelims = c(18,150), research.question = "Wie alt waren die Patienten, ohne Minderjährige, R1")
discovery.tool(2, dependent.variable = "age", agelims = c(18,150), research.question = "Wie alt waren die Patienten, ohne Minderjährige, R2")
```

```{r}
complete.table<- function(dv){
  browser()
  im<- table(dv)
  days<- as.numeric(names(im))
  Freq<- numeric(max(days))
  Freq[days]<- as.data.frame(im)$dv
  prob<- Freq/sum(Freq)
  return(cbind(seq(1,max(days)),Freq,prob))
}

complete.table(full_r1$no.matches_diag)

table(full_r1$no.matches_diag)
prop.table(table(full_r1$no.matches_diag))
table(full_r2$no.matches_diag)
prop.table(table(full_r2$no.matches_diag))

table(-full_r1$start_date+full_r1$labtest)
table(-full_r2$start_date+full_r2$labtest)

table(-full_r1$start_date+full_r1$blood_normal)
table(-full_r2$start_date+full_r2$blood_normal)

table(-full_r1$start_date+full_r1$CRP)
table(-full_r2$start_date+full_r2$CRP)

table(-full_r1$start_date+full_r1$procalcitonin)
table(-full_r2$start_date+full_r2$procalcitonin)

table(-full_r1$start_date+full_r1$leuko)
table(-full_r2$start_date+full_r2$leuko)

table(-full_r1$start_date+full_r1$Uberw_Pneumo)
table(-full_r2$start_date+full_r2$Uberw_Pneumo)

table(-full_r1$start_date+full_r1$Uberw_Radiol)
table(-full_r2$start_date+full_r2$Uberw_Radiol)

table(-full_r1$start_date+full_r1$Uberw_KH)
table(-full_r2$start_date+full_r2$Uberw_KH)
```

