---
title: "04.12.23"
author: "Raphael Kroes"
date: "2023-12-04"
output: html_document
---

Procedure:
1. Clear work space & load packages
2. Read in all data and all functions
3. Optional: remove unnecessary data from workspace
5. Check whether multiple entries for the same date/ patient are in the data sets & deal with them
7. 
```{r}
# 1 Clear work space & load packages
rm(list=ls())
library(readxl)
library(dplyr)
library(parallel)
library(lubridate)
library(ggplot2)
library(writexl)
```

```{r}
# 2
# Read in data
setwd("N:/StudentischeHilfskraefte/_Kroes (Christoph)/Routinedaten/01_Husten/DB")
#names.vec<- c("Diag3","Impf3","IPC23","Labor3","LU3","PZN3","Stamm3","Ueberweis3")
names.vec<- c("Diag3","IPC23","Labor3","LU3","PZN3","Stamm3","Ueberweis3")

for (i in seq(1,length(names.vec))) {
  file.name<- paste0("DB_",names.vec[i],"_v03",".csv")
  im.file<- read.csv(file = file.name, header = TRUE, sep = ";")

  assign(names.vec[i],im.file)

}
# remove duplicate file and unnecessary name
rm(file.name,im.file)

# Read in supplementary data
ListeKrankenkassen<- read.csv(file = "ListeKrankenkassen.csv", header = TRUE, sep = ";")
altersstruktur_deutschland <- read_excel("altersstruktur deutschland.xlsx")
icd10_blocks <- read_excel("icd10_blocks.xlsx")
icd10_description<- read_excel("icd10_description.xlsx")

# read in functions
source("//fileserver1.uni-luebeck.de/ifa_homes/raphaelkroes/Documents/GitHub/Code_UKSH_Husten/functions.R")


```

```{r}
# 3
# The patient with unipatID 2 (PatID=1 and index=1) has two dates of birth and shows the hallmarks of a test patient (e.g. for testing new computer equipment). Whatever the reason for the two different dates, we remove them from further data analysis.

diag.up<- Diag3 |> 
  select(uniPatID,TG_DateNum,DiagTyp,icd10)|>
  distinct()
#diag.up$uniPatID<- as.factor(diag.up$uniPatID)
#diag.up$DiagTyp<- as.factor(diag.up$DiagTyp)
diag.up<- diag.up[diag.up$uniPatID!=2,]
diag.up$chronic<- as.character(diag.up$DiagTyp)
#add variable for chronic disease
diag.up$chronic[diag.up$chronic=="DD"]<- 1
diag.up$chronic[diag.up$chronic!="1"]<- 0
diag.up$chronic<- as.numeric(diag.up$chronic)
diag.up$chronic[is.na(diag.up$chronic)]<- 0

copd.vec<- as.character(levels(as.factor(diag.up$uniPatID[grepl("J44",diag.up$icd10)])))

# impf.up<- Impf3|> 
#   select(uniPatID,TG_DateNum,Influenza,starts_with("Cov"))|>
#   distinct()
# impf.up$uniPatID<- as.factor(impf.up$uniPatID)
# impf.up<- impf.up[impf.up$uniPatID!=2,]

ipc.up<- IPC23 |>
  select(uniPatID,TG_DateNum,AnamnTyp,ipc2)
#ipc.up$uniPatID<- as.factor(ipc.up$uniPatID)
#ipc.up$AnamnTyp<- as.factor(ipc.up$AnamnTyp)
ipc.up<- ipc.up[ipc.up$uniPatID!=2,]

labor.up<- Labor3
labor.up$labtest<- 1
labor.up<- labor.up|>
  select(uniPatID,TG_DateNum,Untersuchung,Wertnum,NormLB,NormUB,labtest) |>
  filter(Untersuchung=="KREA")#change to more reasonable inspection: Blutbild, CRP, Erythrozytenzahl/Leukozytenzahl, Procalcitonin
labor.up$KREA_unter<- as.numeric(labor.up$Wertnum<labor.up$NormLB)
labor.up$KREA_ueber<- as.numeric(labor.up$Wertnum>labor.up$NormUB)
labor.up<- labor.up|>
  select(uniPatID,TG_DateNum,KREA_unter,KREA_ueber)|>
  distinct()
#labor.up$uniPatID<- as.factor(labor.up$uniPatID)
labor.up<- labor.up[labor.up$uniPatID!=2,]

lu.up<- LU3|> 
  select(uniPatID,TG_DateNum)|>
  distinct()
lu.up$lu.dummy<- 1
#lu.up$uniPatID<- as.factor(lu.up$uniPatID)
lu.up<- lu.up[lu.up$uniPatID!=2,]

pzn.up<- PZN3 |> 
  select(uniPatID,TG_DateNum,PZN) |> 
  filter(TG_DateNum>0)|>
  distinct()
#pzn.up$uniPatID<- as.factor(pzn.up$uniPatID)
#pzn.up$PZN<- as.factor(pzn.up$PZN)
pzn.up<- pzn.up[pzn.up$uniPatID!=2,]

stamm.up<- Stamm3
stamm.up$PKV<- IK2PKV(stamm.up$IK)
stamm.up<- stamm.up|> 
  filter(IK>0)|>
  select(-PatID,-index_i,-IK,-Kasse,-PLZ)|>
  distinct()|>
  arrange(uniPatID,desc(TG_DateNum))
#stamm.up$uniPatID<- as.factor(stamm.up$uniPatID)
stamm.up<- stamm.up[stamm.up$uniPatID!=2,]

ueberweis.up<- Ueberweis3|>
  select(uniPatID,TG_DateNum,Uberw_Pneumo,Uberw_Radiol,Uberw_KH) |>
  filter(Uberw_Pneumo>0|Uberw_Radiol>0|Uberw_KH>0)|>
  distinct()
#ueberweis.up$uniPatID<- as.factor(ueberweis.up$uniPatID)
ueberweis.up<- ueberweis.up[ueberweis.up$uniPatID!=2,]
```


```{r}
# 4 free up memory by clearing the original, raw datasets out
rm(list = names.vec)
```

```{r}
# 5
contains.multiple.entries(diag.up)
contains.multiple.entries(impf.up)
contains.multiple.entries(ipc.up)
contains.multiple.entries(labor.up)
contains.multiple.entries(lu.up)
contains.multiple.entries(pzn.up)
contains.multiple.entries(stamm.up)
contains.multiple.entries(ueberweis.up)

```

STOP: Every patient/date combination must be unique. The difference between number of rows and patient/ time combinations must therefore be 0. This is what contains.multiple.entries checks for. We believe diag.up, ipc.up, and pzn.up have multiple entries for the same date by design. We believe stamm.up, impf.up, labor.up, and ueberweis.up should have only one line per patient/ time combination. In #6.1 we remedy the presumed errors by selecting the last entry for each patient/ time combination. In #6.2 we write the multiple data points of diag.up, ipc.up, and pzn.up in additional columns. Both procedures leave us with unique date/ time combinations for each data set.
In #6.2, we do not keep all entries for diag.up and ipc.up. There are a few entries with unreasonably high numbers of diagnoses or symptoms. Therefore, we truncate the number observations at the 95% quantile of the distribution of entries per combination. If the last sentence is not clear in meaning, please run the commented code in chunk #6.2 to gain better insight.
```{r}
# 5.1
# impf.up<- data.repair(impf.up)
# contains.multiple.entries(impf.up)

labor.up<- data.repair(labor.up)
contains.multiple.entries(labor.up)

stamm.up<- data.repair(stamm.up)
contains.multiple.entries(stamm.up)

ueberweis.up<- data.repair(ueberweis.up)
contains.multiple.entries(ueberweis.up)

```


```{r}
# 5.2
x_diag<- quantile(table(paste(diag.up$uniPatID,diag.up$TG_DateNum)), probs= 0.95)
x_ipc<- quantile(table(paste(ipc.up$uniPatID,ipc.up$TG_DateNum)), probs= 0.95)
x_pzn<- quantile(table(paste(pzn.up$uniPatID,pzn.up$TG_DateNum)), probs= 1)

# table(paste0(diag.up$uniPatID,diag.up$TG_DateNum)
# quantile(table(paste0(diag.up$uniPatID,diag.up$TG_DateNum)))

diag.up_2<- aligner.parallel.new(diag.up, x_diag,100,4)
contains.multiple.entries(diag.up_2)

ipc.up_2<- aligner.parallel.new(ipc.up, x_ipc,100,4)
contains.multiple.entries(ipc.up_2)

pzn.up_2<- aligner.parallel.new(pzn.up, x_pzn,100,4)
contains.multiple.entries(pzn.up_2)



```

```{r}
# 6 create episodes based on the data
episodes<- episode.fun.new(ipc.up_2,56)
```

There must be no overlap in the timing of the episodes in order to map diagnoses and treatments to the episodes.
There is no decision rule we can enforce that distinguishes perfectly whether episodes match or match not. Therefore, we implement different decision rules.

```{r}
#decision rule 1: If the timing of episodes overlaps, we treat them as one episode
#decision rule 2: If the timing of episodes overlaps, we treat them as two distinct episodes. The last day of the earlier episode is the day before the new episode begins.
#decision rule 3: For every episode, we select the end date as the earlier of the following two: (1) the previously selected maximum length of episode, (2) the next recorded symptom or batch of symptoms which is not cough (R05).
#decision rule 4: If the timing of episodes overlaps, we check whether there is a change in quarter between those two visits. If there is a change, we treat them as one and use the first incident's end date, otherwise we set the last day of the earlier episode to be last day of the quarter.
#decision rule 5: Combination of rules 3 and 4. If there is an overlap between episodes, we consider them as one if the quarter ends between the two records. However, if symptoms are recorded between these dates which are not cough, the first episode ends with the day before the new symptoms- even if the quarter ends between these days.


#check rule3: does it also cut off for dates before the overlapping time? Because it should by our rationale
#test for functionality/ troubleshoot
# no. 20
episodes.dr3<- function(episodedf,ipc, debug=FALSE){
  # Applies decision rule 3 to a raw (i.e. containing overlapping episodes) episode data frame.
  patients<- levels(as.factor(episodedf$uniPatID))
  next.incident<- numeric(nrow(episodedf))
  for(i in seq(1,length(patients))){
    pat_i<- patients[i]
    rows.episodes<- which(episodedf$uniPatID==pat_i)
    start.dates.episodes<- episodedf$start_date[rows.episodes]
    end.dates.episodes<- episodedf$end_date[rows.episodes]
    incident.dates<- ipc$TG_DateNum[ipc$uniPatID==pat_i]
    store<- numeric(length(start.dates.episodes))
    for(j in seq(1, length(start.dates.episodes))){
      indices<- which(incident.dates> start.dates.episodes[j] & incident.dates<end.dates.episodes[j])
      if(length(indices)>0){
        store[j]<- min(incident.dates[indices])
      }else{
        store[j]<- end.dates.episodes[j]
      }
    }
    next.incident[rows.episodes]<- store
  }
  
  if(debug==TRUE){
    out<- cbind(episodedf,next.incident)
  }else{
    out<- episodedf
    out$end_date<- next.incident
  }
  return(out)
}
episodes.dr3<- function(episodedf,ipc){
  out<- episodedf
  patients<- levels(as.factor(as.character(episodedf$uniPatID)))
  incident.dates<- list()
  pb<- txtProgressBar(min = 1, max = length(patients))
  for(i in seq_along(patients)){
    setTxtProgressBar(pb,i)
    incident.dates[[i]]<- sort(ipc$TG_DateNum[ipc$uniPatID==patients[i]])
  }
  close(pb)
  
  pb<- txtProgressBar(min = 1, max = nrow(episodedf))
  for(i in seq(1,nrow(episodedf))){
    setTxtProgressBar(pb,i)
    pat<- episodedf$uniPatID[i]
    incidents.pat<- c(incident.dates[[which(patients==pat)]],NA)
    day.before.next.incident<- incidents.pat[which(episodedf$start_date[i]==incidents.pat)+1]-1
    out$end_date[i]<- min(episodedf$end_date[i],day.before.next.incident, na.rm = TRUE)
  }
  close(pb)
  return(out)
}
episodes_r3<- episodes.dr3(episodes,ipc.up_2)



#work in progress
episodes.dr5<- function(episodedf,ipc, debug=FALSE){
  # Applies decision rule 5 to a raw (i.e. containing overlapping episodes) episode data frame.
  patients<- levels(as.factor(episodedf$uniPatID))
  next.incident<- numeric(nrow(episodedf))
  for(i in seq(1,length(patients))){
    pat_i<- patients[i]
    rows.episodes<- which(episodedf$uniPatID==pat_i)
    start.dates.episodes<- episodedf$start_date[rows.episodes]
    end.dates.episodes<- episodedf$end_date[rows.episodes]
    incident.dates<- ipc$TG_DateNum[ipc$uniPatID==pat_i]
    store<- numeric(length(start.dates.episodes))
    for(j in seq(1, length(start.dates.episodes))){
      indices<- which(incident.dates> start.dates.episodes[j] & incident.dates<end.dates.episodes[j])
      if(length(indices)>0){
        store[j]<- min(incident.dates[indices])
      }else{
        store[j]<- end.dates.episodes[j]
      }
    }
    next.incident[rows.episodes]<- store
  }
  
  if(debug==TRUE){
    out<- cbind(episodedf,next.incident)
  }else{
    out<- episodedf
    out$end_date<- next.incident
  }
  return(out)
}

episodes.overlap.finder<- function(episodedf, date=FALSE){
  n<- nrow(episodedf)
  overlap<- numeric(n)
  for(i in seq(2,n)){
    if(episodedf$uniPatID[i]==episodedf$uniPatID[i-1]){
      if(episodedf$start_date[i]<episodedf$end_date[i-1]){
        overlap[i]<- 1
      }
    }
  }
  out<- episodedf
  out$overlap<- overlap
  if(date==TRUE){
    out$start_date<- TG_DateNum2date(out$start_date)
    out$end_date<- TG_DateNum2date(out$end_date)
  }
  return(out)
}
```
```{r}
# 7 create non-overlapping episodes
episodes_r1<- episodes.dr1(episodes)
episodes_r2<- episodes.dr2(episodes)
# episodes_r3<- episodes.dr3(episodes,ipc.up_2)
# episodes_r4<- episodes.dr4(episodes)
#episodes_r5<- episodes.dr5(episodes)

# test for how many overlaps there are
sum(episodes.overlap.finder(episodes_r1)$overlap)
sum(episodes.overlap.finder(episodes_r2)$overlap)
# sum(episodes.overlap.finder(episodes_r3)$overlap)
# sum(episodes.overlap.finder(episodes_r4)$overlap)
#sum(episodes.overlap.finder(episodes_r5)$overlap)

```

```{r}
# 8 merge patient outcome data to episodes
episodes_r1<- add.stamm.new(episodes_r1,stamm.up)
episodes_r2<- add.stamm.new(episodes_r2,stamm.up)
# episodes_r3<- add.stamm.new(episodes_r3,stamm.up)
# episodes_r4<- add.stamm.new(episodes_r4,stamm.up)
#episodes_r5<- add.stamm.new(episodes_r5,stamm.up)

full_r1<- add.dataset(episodes_r1,diag.up_2,"diagnoses")

#create full data episode data frames
rules<- c(1,2)
ticker<- 0
for(i in rules){#right now, only four decision rules are available
  im<- add.dataset(get(paste0("episodes_r",i)),diag.up_2,"diagnoses")
  ticker<- ticker+1
  print(ticker)
  # im<- add.dataset(im,impf.up,"impf")
  # ticker<- ticker+1
  # print(ticker)
  im<- add.dataset(im,labor.up,"lab")
  ticker<- ticker+1
  print(ticker)
  im<- add.dataset(im,lu.up,"lu")
  ticker<- ticker+1
  print(ticker)
  # im<- add.dataset(im,pzn.up_2,"pzn")
  # ticker<- ticker+1
  # print(ticker)
  im<- add.dataset(im,ueberweis.up,"ueberweis")
  ticker<- ticker+1
  print(ticker)

  assign(paste0("full.data.episodes_r",i),im)
}
rm(im)

```

```{r}
add.dataset.new<- function(episodedf, adddata, no.splits, no.cores, suffix){
  patients.episodedf<- levels(as.factor(as.character(episodedf$uniPatID)))
  preselector<- as.character(adddata$uniPatID) %in% patients.episodedf
  im<- adddata[preselector,]
  im<- chunk.data(im,no.splits)
  
  distinct.environment<- environment()
  adddata.cluster<- makeCluster(no.cores)
  clusterExport(adddata.cluster, varlist = c("im"), envir = distinct.environment)
  result.list<- parSapply(adddata.cluster,seq(1,no.splits),function(i){
    new.data<- im[[i]]
    entry.match<- numeric(nrow(new.data))
    for(i in seq_along(entry.match)){
      pat<- episodedf$uniPatID==new.data$uniPatID[i]
      start.check<- episodedf$start_date<=new.data$TG_DateNum
      end.check<- episodedf$end_date>=new.data$TG_DateNum
      entry.match[i]<- which(pat&start.check&end.check)
    }
    return(entry.match)
  })
  out<- cbind(episodedf,as.data.frame(matrix(NA,nrow = nrow(episodedf), ncol = ncol(adddata)-2)))
  col.selector<- colnames(adddata)!= "uniPatID" & colnames(adddata)!= "TG_DateNum"
  for(i in seq(1,no.splits)){
    for (j in seq(1,length(result.list[[i]]))) {
      if(result.list[[i]][j]!=0){
        out[,4:ncol(out)]<- im[[i]][j,col.selector]
      }
    }
  }
  return(out)
}
dataset.addition<- function(episodedf, df, no.splits, no.cores, suffix){
  episode.dl<- chunk.data(episodedf,no.splits)
  adddata.dl<- chunk.addata(episode.dl,df)
  
  suffix<- suffix
  dinstinct.environment<- environment()
  add.cluster<- makeCluster(no.cores)
  clusterExport(add.cluster,c("episode.dl","adddata.dl", "suffix"),distinct.environment)
  result.list<- parSapply(add.cluster,1:no.splits, function(j){
    n<- nrow(episode.dl[[j]])
    p<- nrow(adddata.dl[[1]])
    no.matches<- numeric(n)
    
    df_1<- episode.dl[[j]]|>
      arrange(uniPatID)
    addition<- as.data.frame(matrix(NA,nrow = n, ncol = 2*p-4))
    
    pat<- df_1$uniPatID[1]
    df_2<- adddata.dl[[j]]|>
      filter(uniPatID==pat)|>
      arrange(TG_DateNum)
    selector<- which(df_2$TG_DateNum >= df_1$start_date[1] & df_2$TG_DateNum >= df_1$end_date[1])
    if(length(selector)>=1){
      addition[1,seq(1,p-2)]<- df_2[min(selector),]|>
        select(-uniPatID,-TG_DateNum)
      addition[p-1,ncol(addition)]<- df_2[max(selector),]|>
        select(-uniPatID,-TG_DateNum)
      no.matches[1]<- length(selector)
    }
    
    for(i in seq(2,n)){
      if(df_1$uniPatID[i]!=df_1$uniPatID[i-1]){
        pat<- df_1$uniPatID[i]
        df_2<- adddata.dl[[j]]|>
          filter(uniPatID==pat)|>
          arrange(TG_DateNum)
      }
      selector<- which(df_2$TG_DateNum >= df_1$start_date[i] & df_2$TG_DateNum >= df_1$end_date[i])
      if(length(selector)>=1){
        addition[1,seq(1,p-2)]<- df_2[min(selector),]|>
          select(-uniPatID,-TG_DateNum)
        addition[p-1,ncol(addition)]<- df_2[max(selector),]|>
          select(-uniPatID,-TG_DateNum)
        no.matches[i]<- length(selector)
      }
    }
    out<- cbind(df_1,addition,no.matches)
    add.colnames<- colnames(adddata.dl[[1]])
    add.colnames<- add.colnames[add.colnames!= "uniPatID" & add.colnames!= "TG_DateNum"]
    colnames(out)<- c(colnames(df_1),
                      paste0("first", add.colnames),
                      paste0("last", add.colnames),
                      paste0("no.matches_",suffix))
    return(out)
  })
  
  stopCluster(add.cluster)
  return(result.list)
}
```

```{r}
chunk.adddata<- function(chunkeddl, adddata){
  l<- length(chunkeddl)
  chunked.adddata<- list()
  for(i in seq(1,l)){
    ids<- as.character(chunkeddl[[i]]$uniPatID)
    chunked.adddata[[i]]<- adddata|>
      filter(uniPatID %in% ids)
  }
  return(chunked.adddata)
}
```


```{r}
# 9 extract summary statistics
summary.stats<- function(episodedf){
  no.patients<- length(levels(as.factor(episodedf$uniPatID)))
  no.episodes<- nrow(episodedf)
  numbers<- list(
    no.episodes= nrow(episodedf),
    no.patients= length(levels(as.factor(episodedf$uniPatID))),
    no.stammdata.there= sum(episodedf$stamm_is_there, na.rm = TRUE),
    earliest.recorded.cough= TG_DateNum2date(min(episodedf$start_date)),
    latest.recorded.cough= TG_DateNum2date(max(episodedf$start_date)),
    no.males=sum(episodedf$Maennl, na.rm = TRUE),
    no.females=sum(episodedf$Weibl, na.rm = TRUE),
    no.transgender=sum(episodedf$Transgen, na.rm = TRUE),
    no.undefined.sex=sum(episodedf$Geschlechtundef, na.rm = TRUE),
    
    average.no.visit.per.patient=nrow(episodedf)/no.patients,
    percentage.stammdata.there= sum(episodedf$stamm_is_there, na.rm = TRUE)/no.episodes,
    percentage.males=sum(episodedf$Maennl, na.rm = TRUE)/no.episodes,
    percentage.females=sum(episodedf$Weibl, na.rm = TRUE)/no.episodes,
    percentage.transgender=sum(episodedf$Transgen, na.rm = TRUE)/no.episodes,
    percentage.undefined.sex=sum(episodedf$Geschlechtundef, na.rm = TRUE)/no.episodes,
    percentage.private.insurance= mean(episodedf$PKV, na.rm= TRUE),
    percentageretired= mean(episodedf$Status_R, na.rm= TRUE)
  )
  return(numbers)
}

```

```{r}
discovery.tool<- function(decision.rule, pandemic="none", insurance=c("all","GKV","PKV")[1], remove.copd=FALSE, dependent.variable, research.question){
  # Tool to create plots and tables for specific data requests.
  # decision.rule is an integer between 1 and 5 giving the decision rule for how to deal with overlaps in the data set.
  # pandemic: if specified, set it to TRUE if only pandemic data is to be analysed, and to false if only data before the pandemic is to be included.
  # dependent.variable specifies the dependent variable to be looked at.
  # constraint.list is a list of constraints what cases are to be selected.
  # research.question is the question that the plot/ table aims to answer. It is used as label for the plot and is used to name the generated files. Therefore, it must not contain any kind of punctuation (only underline permitted)! The function adds a question mark automatically at the end of each label with the research question!
  
  
  # 1. setup of parameters and data
  if(decision.rule==1){
    episodedf<- full.data.episodes_r1
  }else if(decision.rule==2){
    episodedf<- full.data.episodes_r2
  }else if(decision.rule==3){
    episodedf<- full.data.episodes_r3
  }else if(decision.rule==4){
    episodedf<- full.data.episodes_r4
  }else if(decision.rule==5){
    episodedf<- full.data.episodes_r5
  }else{
    stop("The decision rule must be an integer between 1 and 5!")
  }
  
  if(insurance=="PKV"){
    episodedf<- episodedf[episodedf$PKV==1,]
  }else if(insurance=="GKV"){
    episodedf<- episodedf[episodedf$PKV==0,]
  }
  
  if(remove.copd){
    keep.vec<- numeric(nrow(episodedf))
    for(i in seq(1,nrow(episodedf))){
      if(episodedf$uniPatID[i] %in% copd.vec){
        keep.vec[i]<- FALSE
      }else{
        keep.vec[i]<- TRUE
      }
    }
    episodedf<- episodedf[keep.vec,]
  }
  
  earliest.TG_Date<- min(episodedf$start_date)
  latest.TG_Date<- max(episodedf$start_date)
  earliest.year.POSIXlt<- year(TG_DateNum2date(earliest.TG_Date))
  latest.year.POSIXlt<- year(TG_DateNum2date(latest.TG_Date))
  no.years<- latest.year.POSIXlt-earliest.year.POSIXlt
  pandemic.start<- date2TG_DateNum("2020-01-01")
  pandemic.end<- date2TG_DateNum("2023-01-01")
  length.pandemic<- 3
  
  if(pandemic==TRUE){
    episodedf<- episodedf[episodedf$start_date>=pandemic.start & episodedf$start_date<pandemic.end,]
  }else if(pandemic==FALSE){
    episodedf<- episodedf[episodedf$start_date<pandemic.start,]
  }else if(pandemic=="none"){
    #nothing happens
  }else{
    stop("pandemic must be specified as TRUE, FALSE, or be non-specified.")
  }
  
  #creating plots and tables
  
  #####diag#####diag#####diag#####diag#####diag#####diag#####diag#####diag#####diag#####diag#####diag#####diag#####diag#####diag#####diag#####diag#####diag#####diag#####diag#####diag
  if(dependent.variable=="diag"){
    if(diag.parameters[["initial.or.last"]]=="last"){
      all.diagnoses<- as.vector(as.matrix(episodedf[,grepl("last_icd10", colnames(episodedf))]))
    }else if(diag.parameters[["initial.or.last"]]=="initial"){
      all.diagnoses<- as.vector(as.matrix(episodedf[,grepl("first_icd10", colnames(episodedf))]))
    }else{
      stop("initial.or.last in diag.parameters is incorrectly specified")
    }
    
    all.diagnoses<- all.diagnoses[!is.na(all.diagnoses)]
    all.diagnoses<- all.diagnoses[all.diagnoses!="0"]
    
    chapters<- icd10.to.chapter(all.diagnoses)[,2]
    im<- table(chapters)
    chapter.no<- as.numeric(names(im))
    names(im)<- NULL
    prob<- numeric(22)
    prob[chapter.no]<- im
    prob<- prob/sum(prob)
    d.chapter<- data.frame(x=1:22,prob=prob)
    
    
    blocks<- icd10.to.block(all.diagnoses)
    im<- table(blocks[,1])
    blocks.no<- as.numeric(names(im))
    names(im)<- NULL
    prob<- numeric(241)
    prob[blocks.no]<- im
    prob<- prob/sum(prob)
    d.block_num<- data.frame(x=1:241,prob=prob)
    d.block_description<- data.frame(x=icd10_blocks$description, prob=prob)
    
    p<- ggplot(d.chapter, aes(x=x, y=prob)) +
      geom_bar(stat = "identity", fill="skyblue") +
      scale_y_continuous(labels = scales::percent_format()) +
      labs(title = paste0(research.question,"?"),x = "ICD10 chapter", y= "percentage")
    ggsave(paste0(research.question,"_chapter.png"), plot = p, path = getwd(), device = "png")
    
    p<- ggplot(d.block_num, aes(x=x, y=prob)) +
      geom_bar(stat = "identity", fill="skyblue") +
      scale_y_continuous(labels = scales::percent_format()) +
      labs(title = paste0(research.question,"?"),x = "ICD10 block", y= "percentage")
    ggsave(paste0(research.question,"_block_num.png"), plot = p, path = getwd(), device = "png")
    
    p<- ggplot(d.block_description, aes(x=x, y=prob)) +
      geom_bar(stat = "identity", fill="skyblue") +
      scale_y_continuous(labels = scales::percent_format()) +
      labs(title = paste0(research.question,"?"),x = "ICD10 block", y= "percentage")
    ggsave(paste0(research.question,"_block_description.png"), plot = p, path = getwd(), device = "png")
    
    write_xlsx(data.frame(no=1:241,description=icd10_blocks$description, probability=prob),paste0(research.question,".xlsx"))
    
    #####age#####age#####age#####age#####age#####age#####age#####age#####age#####age#####age#####age#####age#####age#####age#####age#####age#####age#####age#####age#####age#####age#####age#####age
    
  }else if(dependent.variable=="age"){
    
    x<- as.numeric(year(TG_DateNum2date(episodedf$start_date)))-episodedf$Geburtsjahr
    if(sum(is.na(x))>0){
      warning(paste("There are",sum(is.na(x)),"entries where no birth date is available. This corresponds to",round(sum(is.na(x))/length(x),2)*100), "% of all entries. The NA results are dropped in the following.")
      x<- x[!is.na(x)]
    }
    max.age<- max(c(100,max(x)))
    im<- table(x)
    ages<- as.numeric(names(im))
    names(im)<- NULL
    prob<- numeric(max.age)
    prob[ages]<- im
    prob<- prob/sum(prob)
    d<- data.frame(x=seq(1,max.age),prob=prob)
    
    d$y<- age.weights(1,max.age)
    
    p<- ggplot(d, aes(x = x)) +
      geom_bar(aes(y = prob, fill = "Patient age"), stat = "identity") +
      geom_line(aes(y = y, color = "Age distribution of Germany")) +
      scale_y_continuous(labels = scales::percent_format()) +
      labs(title = paste0(research.question,"?"),
           x = "Age in years",
           y = "Percentage") +
      scale_fill_manual(values = c("skyblue"), labels = c("Patient age")) +
      scale_color_manual(values = c("red"), labels = c("Age distribution of Germany")) +
      theme(legend.position = "bottom")
    
    ggsave(paste0(research.question,".png"), plot = p, path = getwd(), device = "png")
    
    #####escalation#####escalation#####escalation#####escalation#####escalation#####escalation#####escalation#####escalation#####escalation#####escalation#####escalation#####escalation
    
  }else if(dependent.variable=="escalation"){
    
    if(escalation.parameters[["type"]]==1){
      #blood test
      x<- episodedf$first_TG_DateNumlab-episodedf$start_date
      x<- x[!is.na(x)]
      warning(paste("There are", length(x), "patients whose blood was tested for Kreatinin levels."))
    }else if(escalation.parameters[["type"]]==2){
      #referral to specialist care
      x<- episodedf$first_TG_DateNumueberweis-episodedf$start_date
      x<- x[!is.na(x)]
      warning(paste("There are", length(x), "patients who were referred to a specialist."))
    }else if(escalation.parameters[["type"]]==3){
      #referral pulmonologist
      x<- episodedf$first_TG_DateNumueberweis-episodedf$start_date
      x<- x[episodedf$first_Uberw_Pneumo==1]
      x<- x[!is.na(x)]
      warning(paste("There are", length(x), "patients who were referred to a pulmonologist."))
    }else if(escalation.parameters[["type"]]==4){
      #referral radiologist
      x<- episodedf$first_TG_DateNumueberweis-episodedf$start_date
      x<- x[episodedf$first_Uberw_Radiol==1]
      x<- x[!is.na(x)]
      warning(paste("There are", length(x), "patients who were referred to a radiologist."))
    }else if(escalation.parameters[["type"]]==5){
      #referral hospital
      x<- episodedf$first_TG_DateNumueberweis-episodedf$start_date
      x<- x[episodedf$first_Uberw_KH==1]
      x<- x[!is.na(x)]
      warning(paste("There are", length(x), "patients who were referred to a hospital."))
    }
    
    im<- table(x)
    allocation<- as.numeric(names(im))
    names(im)<- NULL
    prob<- numeric(max(allocation)+1)
    prob[allocation+1]<- im
    prob<- prob/sum(prob)
    d<- data.frame(x=seq(0,max(allocation)),prob=prob)
    
    
    p<- ggplot(d, aes(x=x, y=prob)) +
      geom_bar(stat = "identity", fill="skyblue") +
      scale_y_continuous(labels = scales::percent_format()) +
      labs(title = paste0(research.question,"?"),
           x = "number of days since initial cough", 
           y= "percentage",
           subtitle = paste("based on the observations of", length(x), "patients"))
    ggsave(paste0(research.question,".png"), plot = p, path = getwd(), device = "png")
  }
}

```

```{r}
# 10 data discovery tool
diag.parameters<-list(
  initial.or.last= "last"
)
escalation.parameters<- list(
  type= 1
  #type: 1= blood test for Kreatinin, 2= referral to specialist care (pulmonologist, radiologist, hospital), 3= referral to pulmonologist, 4= referral to radiologist, 5= referral to hospital
)
constraints_1<- list(
  ""
)

escalation.parameters<- list(
  type= 1
  #type: 1= blood test for Kreatinin, 2= referral to specialist care (pulmonologist, radiologist, hospital), 3= referral to pulmonologist, 4= referral to radiologist, 5= referral to hospital
)
#function(decision.rule, pandemic="none", insurance=c("all","GKV","PKV")[1], remove.copd=FALSE, dependent.variable, research.question)
discovery.tool(1,  dependent.variable = "escalation", research.question = "How much time elapsed between the initial cough and a Kreatinin test for publicly insured individuals")
escalation.parameters<- list(
  type= 2
  #type: 1= blood test for Kreatinin, 2= referral to specialist care (pulmonologist, radiologist, hospital), 3= referral to pulmonologist, 4= referral to radiologist, 5= referral to hospital
)
discovery.tool(1,dependent.variable = "escalation", research.question = "How much time elapsed before the GP sent the patient to a specialist")
escalation.parameters<- list(
  type= 3
  #type: 1= blood test for Kreatinin, 2= referral to specialist care (pulmonologist, radiologist, hospital), 3= referral to pulmonologist, 4= referral to radiologist, 5= referral to hospital
)
discovery.tool(1,dependent.variable = "escalation", research.question = "How much time elapsed before the GP sent the patient to a pulmonologist")
escalation.parameters<- list(
  type= 4
  #type: 1= blood test for Kreatinin, 2= referral to specialist care (pulmonologist, radiologist, hospital), 3= referral to pulmonologist, 4= referral to radiologist, 5= referral to hospital
)
discovery.tool(1,dependent.variable = "escalation", research.question = "How much time elapsed before the GP sent the patient to a radiologist")
escalation.parameters<- list(
  type= 5
  #type: 1= blood test for Kreatinin, 2= referral to specialist care (pulmonologist, radiologist, hospital), 3= referral to pulmonologist, 4= referral to radiologist, 5= referral to hospital
)
discovery.tool(1,dependent.variable = "escalation", research.question = "How much time elapsed before the GP sent the patient to the hospital")
```



```{r}
summary.stats(episodedf = episodes_r1_stamm)
summary.stats(episodedf = episodes_r2_stamm)
```
```{r}
summary.plots(full.data.episodes_r1)
```

```{r}
#new stats and plots for Steinhäuser
pkv.summaries<- list()
pkv.summaries[[1]]<- summmary(stamm.up$PKV)
ticker<-2
clinic.ids<- levels(as.factor(stamm.up$PraxisID))
for(i in seq_along(clinic.ids)){
  pkv.summaries[[ticker]]<- summary(stamm.up$PKV[stamm.up$PraxisID==clinic.ids[i]])
}
pkv.summaries
#for overview, add data on the location of the clinic




```
```{r}
dl<- chunk.data(Stamm3,50)
check.cl<- makeCluster(4)
dist.env<- environment()
clusterExport(check.cl,varlist=list(dl),envir=dist.env)
res<- parSapply(check.cl,1:50,function(j){
  l<- levels(as.factor(dl[[j]]$uniPatID))
  id.collector<- numeric(length(l))
  for(i in seq_along(l)){
    id<- l[i]
    loc<- which(dl[[j]]$uniPatID==id)
    if(length(unique(dl[[j]]$Geburtsjahr[loc]))!=1 | length(unique(dl[[j]]$Geburtsmonat[loc]))!=1){
      id.collector[i]<- 1
    }
  }
})

```
```{r}
res<- sapply(1:50,function(j){
  l<- levels(as.factor(dl[[j]]$uniPatID))
  id.collector<- numeric(length(l))
  for(i in seq_along(l)){
    id<- l[i]
    loc<- which(dl[[j]]$uniPatID==id)
    if(length(unique(dl[[j]]$Geburtsjahr[loc]))!=1 | length(unique(dl[[j]]$Geburtsmonat[loc]))!=1){
      id.collector[i]<- 1
    }
  }
})
```
```{r}
df<- Stamm3|>
  arrange(uniPatID)
error.vec.year<- numeric(nrow(df))
error.vec.month<- numeric(nrow(df))
for(i in seq_along(error.vec.year)[-1]){
  if(df$uniPatID[i]==df$uniPatID[i-1]){
    if(!is.na(df$Geburtsjahr[i] & !is.na(df$Geburtsmonat[i]))){
      if(df$Geburtsjahr[i]!=df$Geburtsjahr[i-1]){
        error.vec.year[i]<- 1
      }
      if(df$Geburtsmonat[i]!=df$Geburtsmonat[i-1]){
        error.vec.month[i]<- 1
      }
    }
  }
}
id<- df$uniPatID[-1]
id_lag<- df$uniPatID[-nrow(df)]
na.rmvr<- !is.na(df$Geburtsjahr[-1]) & !is.na(df$Geburtsmonat[-nrow(df)])
yrs<- df$Geburtsjahr[-1]!=df$Geburtsjahr[-nrow(df)]
mnths<- df$Geburtsmonat[-1]!=df$Geburtsmonat[-nrow(df)]
error.vec.year<- as.numeric(id==id_lag & na.rmvr & yrs)
error.vec.month<- as.numeric(id==id_lag & na.rmvr & mnths)
```

```{r}
#list of diseases by icd-10 code
decision.rules<- c(1)
icd10.codes.3<- c()
for(i in decision.rules){
  im<- get(paste0("full.data.episodes_r",i))
  im<- as.vector(as.matrix(im[,grepl("icd10",colnames(im))]))
  im<- im[!is.na(im)]
  im<- im[im!="0"]
  icd10.codes.3<- c(icd10.codes.3,substr(im,1,3),substr(im,1,3))
}
icd10.codes.3<- as.character(levels(as.factor(icd10.codes.3)))
all.diagnosed.bocks<- icd10.to.block(icd10.codes.3)$title
icd10_3digit_description.function<- function(dv){
  out<- numeric(length = length(dv))
  for(i in seq_along(dv)){
    out[i]<- icd10_description$text[which(dv[i]==icd10_description$code)]
  }
  return(out)
}
# check whether icd10_description is a tibble- it should be a df. 
all.diagnosed.diseases<- data.frame(
  ICD10= icd10.codes.3,
  ICD10_description= icd10_description[match(icd10.codes.3,icd10_description[,1]),2],
  Gruppe= all.diagnosed.bocks,
  Kapitel= icd10.to.chapter(icd10.codes.3)[,2]
)
View(all.diagnosed.diseases)

```

```{r}
#dataset creating fun
full.episode.creator<- function(length.of.episode,decision.rule){
  im<- episode.fun.new(ipc.up_2,length.of.episode)
  
}
```

```{r}
# no. 23
add.stamm<- function(episodedf, stamm){
  #adds stamm data to the episode data frame by matching entries.
  #episodedf is a data frame created through one of the decision rules episodes.drx
  #stamm is a cleaned and prepared stamm data frame (e.g. stamm.up_2)
  #The function returns an episode data frame with the Stamm data matched to the episodes. There is also a variable called stamm_is_there, which is 1 if a Stamm entry was able to be matched, and 0 if no Stamm entry was able to be matched to that patient/ episode.
  n<- nrow(episodedf)
  p<- ncol(episodedf)
  p_out<- p+ncol(stamm)
  out<- as.data.frame(matrix(NA, nrow = n, ncol = p_out))
  stamm$uniPatID<- as.character(stamm$uniPatID)
  stamm.is.there<- numeric(n)
  for(i in seq(1,n)){
    pat_i<- as.character(episodedf$uniPatID[i])
    pat.rows<- which(stamm$uniPatID==pat_i)
    if(length(pat.rows)>0){
      dates<- stamm$TG_DateNum[pat.rows]
      im<- dates<=episodedf$start_date[i]
      if(all(!im)){
        #if no Stamm data has been recorded prior to the first coughing (i.e. first visit of clinic), this might be due to the patient being at the clinic for the first time and the doctor back dated the start of coughing (i.e. first health incident, which occurred before the visit visit at the clinic).
        loc<- pat.rows[1]
      }else{
        loc<- pat.rows[sum(im)]
      }
      out[i,seq(p+1,p_out)]<- stamm[loc,]
      stamm.is.there[i]<- 1
    }
  }
  unipat.col<- p+which(colnames(stamm)=="uniPatID")
  #remove duplicate uniPatID column
  out<- out[,-(unipat.col)]
  out[,1:p]<- episodedf
  out<- cbind(out,stamm.is.there)
  colnames(out)<- c(colnames(episodedf),colnames(stamm),"stamm_is_there")[-unipat.col]
  stamm_date.col<- which(colnames(out)=="TG_DateNum")
  colnames(out)[stamm_date.col]<- "Stamm_date"
  return(as.data.frame(out))
}
```





