---
title: "18.07.23"
author: "Raphael Kroes"
date: "2023-07-13"
output: html_document
---

Procedure:
1. Clear work space & load packages
2. Read in all functions (external functions.R file)
3. Read in data
4. Preprocessing I: create correct columns
5. Check whether multiple entries for the same date/ patient are in the data sets
6. Preprocessing II: Deal with multiple entries
7. Create list of data frames
8. Merge data sets
```{r}
# 1-2
rm(list=ls())
library(dplyr)
library(parallel)
# now read in all functions from functions.R file (CTRL+A, CTRL+Enter)
```

```{r}
# 3
# Read in data
setwd("N:/StudentischeHilfskraefte/_Kroes (Christoph)/Routinedaten/01_Husten/DB")

names.vec<- c("Cov3","Diab3","Diag3","DMPChron3","EBM3","EKG3","Impf3","IPC23","Konsul3","Kuerzel3","Labor3","LU3","PZN3","Stamm3","Time3","Ueberweis3","Unters3")


for (i in seq(1,length(names.vec))) {
  file.name<- paste0("DB_",names.vec[i],"_v03",".csv")
  im.file<- read.csv(file = file.name, header = TRUE, sep = ";")

  assign(names.vec[i],im.file)

}
# remove duplicate file and unnecessary name
rm(file.name,im.file)

# adapt this part
ListeKrankenkassen<- read.csv(file = "ListeKrankenkassen.csv", header = TRUE, sep = ";")
```

```{r}
# 4
# continue to filter with distinct!
labor.up<- Labor3|>
  select(uniPatID,TG_DateNum,Untersuchung,Wertnum,NormLB,NormUB) |>
  filter(Untersuchung=="KREA")
labor.up$KREA_unter<- as.numeric(labor.up$Wertnum<labor.up$NormLB)
labor.up$KREA_ueber<- as.numeric(labor.up$Wertnum>labor.up$NormUB)
labor.up<- labor.up|>
  select(uniPatID,TG_DateNum,KREA_unter,KREA_ueber)|>
  distinct()

ueberweis.up<- Ueberweis3|>
  select(uniPatID,TG_DateNum,Uberw_Pneumo,Uberw_Radiol,Uberw_KH) |>
  filter(Uberw_Pneumo>0|Uberw_Radiol>0|Uberw_KH>0)|>
  distinct()

stamm.up<- Stamm3
stamm.up$PKV<- IK2PKV(stamm.up$IK)
stamm.up<- stamm.up|> 
  select(-PatID,-index_i,-IK,-Kasse)|>
  distinct()

ipc.up<- IPC23 |>
  select(uniPatID,TG_DateNum,AnamnTyp,ipc2)

diag.up<- Diag3 |> 
  select(uniPatID,TG_DateNum,DiagTyp,icd10)|>
  distinct

lu.up<- LU3|> 
  select(uniPatID,TG_DateNum)|>
  distinct()
lu.up$lu.dummy<- 1

impf.up<- Impf3|> 
  select(uniPatID,TG_DateNum,Influenza,starts_with("Cov"))|>
  distinct()

pzn.up<- PZN3 |> 
  select(uniPatID,TG_DateNum,PZN) |> 
  filter(TG_DateNum>0)|>
  distinct()

```
```{r}
# 5
contains.multiple.entries(ipc.up)
contains.multiple.entries(labor.up)
contains.multiple.entries(ueberweis.up)
contains.multiple.entries(stamm.up)
contains.multiple.entries(diag.up)
contains.multiple.entries(lu.up)
contains.multiple.entries(impf.up)
contains.multiple.entries(pzn.up)

```
STOP: code must be adapted if any line (except for icp.up) returns TRUE
```{r}
# 6
im<- ipc.filter(ipc.up)
ipc.up<- im[[1]]
ipc.reference.matrix<- im[[2]]

# im<- ipc.filter(diag.up)
# diag.up<- im[[1]]
# diag.reference.matrix<- im[[2]]
```

```{r}
# 7
merger.list<- list(
  ipc.up,
  labor.up,
  ueberweis.up,
  stamm.up,
  diag.up,
  lu.up,
  impf.up,
  pzn.up
)

```

```{r}
# 8
merged.data.set<- par.patient.file(merger.list)
```





