---
title: "16.11.23"
author: "Raphael Kroes"
date: "2023-11-16"
output: html_document
---

Procedure:
1. Clear work space & load packages
2. Read in all data and all functions
3. Optional: remove unnecessary data from workspace
5. Check whether multiple entries for the same date/ patient are in the data sets & deal with them
7. 
```{r}
# 1 Clear work space & load packages
rm(list=ls())
library(readxl)
library(dplyr)
library(parallel)
library(lubridate)
library(ggplot2)
library(writexl)
```

```{r}
# 2
# Read in data
setwd("N:/StudentischeHilfskraefte/_Kroes (Christoph)/Routinedaten/01_Husten/DB")
names.vec<- c("Diag3","Impf3","IPC23","Labor3","LU3","PZN3","Stamm3","Ueberweis3")


for (i in seq(1,length(names.vec))) {
  file.name<- paste0("DB_",names.vec[i],"_v03",".csv")
  im.file<- read.csv(file = file.name, header = TRUE, sep = ";")

  assign(names.vec[i],im.file)

}
# remove duplicate file and unnecessary name
rm(file.name,im.file)

# Read in supplementary data
ListeKrankenkassen<- read.csv(file = "ListeKrankenkassen.csv", header = TRUE, sep = ";")
altersstruktur_deutschland <- read_excel("altersstruktur deutschland.xlsx")
icd10_blocks <- read_excel("icd10_blocks.xlsx")
icd10_description<- read_excel("icd10_description.xlsx")

# read in functions
source("//fileserver1.uni-luebeck.de/ifa_homes/raphaelkroes/Documents/GitHub/Code_UKSH_Husten/functions.R")


```

```{r}
# 3
# The patient with unipatID 2 (PatID=1 and index=1) has two dates of birth and shows the hallmarks of a test patient (e.g. for testing new computer equipment). Whatever the reason for the two different dates, we remove them from further data analysis.

diag.up<- Diag3 |> 
  select(uniPatID,TG_DateNum,DiagTyp,icd10)|>
  distinct()
diag.up$uniPatID<- as.factor(diag.up$uniPatID)
diag.up$DiagTyp<- as.factor(diag.up$DiagTyp)
diag.up<- diag.up[diag.up$uniPatID!=2,]

impf.up<- Impf3|> 
  select(uniPatID,TG_DateNum,Influenza,starts_with("Cov"))|>
  distinct()
impf.up$uniPatID<- as.factor(impf.up$uniPatID)
impf.up<- impf.up[impf.up$uniPatID!=2,]

ipc.up<- IPC23 |>
  select(uniPatID,TG_DateNum,AnamnTyp,ipc2)
ipc.up$uniPatID<- as.factor(ipc.up$uniPatID)
ipc.up$AnamnTyp<- as.factor(ipc.up$AnamnTyp)
ipc.up<- ipc.up[ipc.up$uniPatID!=2,]

labor.up<- Labor3|>
  select(uniPatID,TG_DateNum,Untersuchung,Wertnum,NormLB,NormUB) |>
  filter(Untersuchung=="KREA")
labor.up$KREA_unter<- as.numeric(labor.up$Wertnum<labor.up$NormLB)
labor.up$KREA_ueber<- as.numeric(labor.up$Wertnum>labor.up$NormUB)
labor.up<- labor.up|>
  select(uniPatID,TG_DateNum,KREA_unter,KREA_ueber)|>
  distinct()
labor.up$uniPatID<- as.factor(labor.up$uniPatID)
labor.up<- labor.up[labor.up$uniPatID!=2,]

lu.up<- LU3|> 
  select(uniPatID,TG_DateNum)|>
  distinct()
lu.up$lu.dummy<- 1
lu.up$uniPatID<- as.factor(lu.up$uniPatID)
lu.up<- lu.up[lu.up$uniPatID!=2,]

pzn.up<- PZN3 |> 
  select(uniPatID,TG_DateNum,PZN) |> 
  filter(TG_DateNum>0)|>
  distinct()
pzn.up$uniPatID<- as.factor(pzn.up$uniPatID)
pzn.up$PZN<- as.factor(pzn.up$PZN)
pzn.up<- pzn.up[pzn.up$uniPatID!=2,]

stamm.up<- Stamm3
stamm.up$PKV<- IK2PKV(stamm.up$IK)
stamm.up<- stamm.up|> 
  filter(IK>0)|>
  select(-PatID,-index_i,-IK,-Kasse,-PLZ)|>
  distinct()|>
  arrange(uniPatID,desc(TG_DateNum))
stamm.up$uniPatID<- as.factor(stamm.up$uniPatID)
stamm.up<- stamm.up[stamm.up$uniPatID!=2,]

ueberweis.up<- Ueberweis3|>
  select(uniPatID,TG_DateNum,Uberw_Pneumo,Uberw_Radiol,Uberw_KH) |>
  filter(Uberw_Pneumo>0|Uberw_Radiol>0|Uberw_KH>0)|>
  distinct()
ueberweis.up$uniPatID<- as.factor(ueberweis.up$uniPatID)
ueberweis.up<- ueberweis.up[ueberweis.up$uniPatID!=2,]
```


```{r}
# 4 free up memory by clearing the original, raw datasets out
rm(list = names.vec)
```

```{r}
# 5
contains.multiple.entries(diag.up)
contains.multiple.entries(impf.up)
contains.multiple.entries(ipc.up)
contains.multiple.entries(labor.up)
contains.multiple.entries(lu.up)
contains.multiple.entries(pzn.up)
contains.multiple.entries(stamm.up)
contains.multiple.entries(ueberweis.up)

```

STOP: Every patient/date combination must be unique. The difference between number of rows and patient/ time combinations must therefore be 0. This is what contains.multiple.entries checks for. We believe diag.up, ipc.up, and pzn.up have multiple entries for the same date by design. We believe stamm.up, impf.up, labor.up, and ueberweis.up should have only one line per patient/ time combination. In #6.1 we remedy the presumed errors by selecting the last entry for each patient/ time combination. In #6.2 we write the multiple data points of diag.up, ipc.up, and pzn.up in additional columns. Both procedures leave us with unique date/ time combinations for each data set.
In #6.2, we do not keep all entries for diag.up and ipc.up. There are a few entries with unreasonably high numbers of diagnoses or symptoms. Therefore, we truncate the number observations at the 95% quantile of the distribution of entries per combination. If the last sentence is not clear in meaning, please run the commented code in chunk #6.2 to gain better insight.
```{r}
# 5.1
impf.up<- data.repair(impf.up)
contains.multiple.entries(impf.up)

labor.up<- data.repair(labor.up)
contains.multiple.entries(labor.up)

stamm.up<- data.repair(stamm.up)
contains.multiple.entries(stamm.up)

ueberweis.up<- data.repair(ueberweis.up)
contains.multiple.entries(ueberweis.up)

```


```{r}
# 5.2
x_diag<- quantile(table(paste(diag.up$uniPatID,diag.up$TG_DateNum)), probs= 0.95)
x_ipc<- quantile(table(paste(ipc.up$uniPatID,ipc.up$TG_DateNum)), probs= 0.95)
x_pzn<- quantile(table(paste(pzn.up$uniPatID,pzn.up$TG_DateNum)), probs= 1)

# table(paste0(diag.up$uniPatID,diag.up$TG_DateNum)
# quantile(table(paste0(diag.up$uniPatID,diag.up$TG_DateNum)))

diag.up_2<- aligner.parallel.new(diag.up, x_diag,100,4)
contains.multiple.entries(diag.up_2)

ipc.up_2<- aligner.parallel.new(ipc.up, x_ipc,100,4)
contains.multiple.entries(ipc.up_2)

pzn.up_2<- aligner.parallel.new(pzn.up, x_pzn,100,4)
contains.multiple.entries(pzn.up_2)



```

```{r}
# 6 create episodes based on the data
episodes<- episode.fun.new(ipc.up_2,56)
```

There must be no overlap in the timing of the episodes in order to map diagnoses and treatments to the episodes.
There is no decision rule we can enforce that distinguishes perfectly whether episodes match or match not. Therefore, we implement different decision rules.

```{r}
#decision rule 1: If the timing of episodes overlaps, we treat them as one episode
#decision rule 2: If the timing of episodes overlaps, we treat them as two distinct episodes. The last day of the earlier episode is the day before the new episode begins.
#decision rule 3: For every episode, we select the end date as the earlier of the following two: (1) the previously selected maximum length of episode, (2) the next recorded symptom or batch of symptoms which is not cough (R05).
#decision rule 4: If the timing of episodes overlaps, we check whether there is a change in quarter between those two visits. If there is a change, we treat them as one and use the first incident's end date, otherwise we set the last day of the earlier episode to be last day of the quarter.
#decision rule 5: Combination of rules 3 and 4. If there is an overlap between episodes, we consider them as one if the quarter ends between the two records. However, if symptoms are recorded between these dates which are not cough, the first episode ends with the day before the new symptoms- even if the quarter ends between these days.


#check rule3: does it also cut off for dates before the overlapping time? Because it should by our rationale
#test for functionality/ troubleshoot
# no. 20
episodes.dr3<- function(episodedf,ipc, debug=FALSE){
  # Applies decision rule 3 to a raw (i.e. containing overlapping episodes) episode data frame.
  patients<- levels(as.factor(episodedf$uniPatID))
  next.incident<- numeric(nrow(episodedf))
  for(i in seq(1,length(patients))){
    pat_i<- patients[i]
    rows.episodes<- which(episodedf$uniPatID==pat_i)
    start.dates.episodes<- episodedf$start_date[rows.episodes]
    end.dates.episodes<- episodedf$end_date[rows.episodes]
    incident.dates<- ipc$TG_DateNum[ipc$uniPatID==pat_i]
    store<- numeric(length(start.dates.episodes))
    for(j in seq(1, length(start.dates.episodes))){
      indices<- which(incident.dates> start.dates.episodes[j] & incident.dates<end.dates.episodes[j])
      if(length(indices)>0){
        store[j]<- min(incident.dates[indices])
      }else{
        store[j]<- end.dates.episodes[j]
      }
    }
    next.incident[rows.episodes]<- store
  }
  
  if(debug==TRUE){
    out<- cbind(episodedf,next.incident)
  }else{
    out<- episodedf
    out$end_date<- next.incident
  }
  return(out)
}
episodes.dr3<- function(episodedf,ipc){
  out<- episodedf
  patients<- levels(as.factor(as.character(episodedf$uniPatID)))
  incident.dates<- list()
  pb<- txtProgressBar(min = 1, max = length(patients))
  for(i in seq_along(patients)){
    setTxtProgressBar(pb,i)
    incident.dates[[i]]<- sort(ipc$TG_DateNum[ipc$uniPatID==patients[i]])
  }
  close(pb)
  
  pb<- txtProgressBar(min = 1, max = nrow(episodedf))
  for(i in seq(1,nrow(episodedf))){
    setTxtProgressBar(pb,i)
    pat<- episodedf$uniPatID[i]
    incidents.pat<- c(incident.dates[[which(patients==pat)]],NA)
    day.before.next.incident<- incidents.pat[which(episodedf$start_date[i]==incidents.pat)+1]-1
    out$end_date[i]<- min(episodedf$end_date[i],day.before.next.incident, na.rm = TRUE)
  }
  close(pb)
  return(out)
}
episodes_r3<- episodes.dr3(episodes,ipc.up_2)

episodes.dr3<- function(episodes,ipc){
  episodes<- episodes|>
    arrange(uniPatID,start_date)
  
}

#work in progress
episodes.dr5<- function(episodedf,ipc, debug=FALSE){
  # Applies decision rule 5 to a raw (i.e. containing overlapping episodes) episode data frame.
  patients<- levels(as.factor(episodedf$uniPatID))
  next.incident<- numeric(nrow(episodedf))
  for(i in seq(1,length(patients))){
    pat_i<- patients[i]
    rows.episodes<- which(episodedf$uniPatID==pat_i)
    start.dates.episodes<- episodedf$start_date[rows.episodes]
    end.dates.episodes<- episodedf$end_date[rows.episodes]
    incident.dates<- ipc$TG_DateNum[ipc$uniPatID==pat_i]
    store<- numeric(length(start.dates.episodes))
    for(j in seq(1, length(start.dates.episodes))){
      indices<- which(incident.dates> start.dates.episodes[j] & incident.dates<end.dates.episodes[j])
      if(length(indices)>0){
        store[j]<- min(incident.dates[indices])
      }else{
        store[j]<- end.dates.episodes[j]
      }
    }
    next.incident[rows.episodes]<- store
  }
  
  if(debug==TRUE){
    out<- cbind(episodedf,next.incident)
  }else{
    out<- episodedf
    out$end_date<- next.incident
  }
  return(out)
}

episodes.overlap.finder<- function(episodedf, date=FALSE){
  n<- nrow(episodedf)
  overlap<- numeric(n)
  for(i in seq(2,n)){
    if(episodedf$uniPatID[i]==episodedf$uniPatID[i-1]){
      if(episodedf$start_date[i]<episodedf$end_date[i-1]){
        overlap[i]<- 1
      }
    }
  }
  out<- episodedf
  out$overlap<- overlap
  if(date==TRUE){
    out$start_date<- TG_DateNum2date(out$start_date)
    out$end_date<- TG_DateNum2date(out$end_date)
  }
  return(out)
}
```
```{r}
# 7 create non-overlapping episodes
episodes_r1<- episodes.dr1(episodes)
episodes_r2<- episodes.dr2(episodes)
episodes_r3<- episodes.dr3(episodes,ipc.up_2,TRUE)
episodes_r4<- episodes.dr4(episodes)
#episodes_r5<- episodes.dr4(episodes)

# test for how many overlaps there are
sum(episodes.overlap.finder(episodes_r1)$overlap)
sum(episodes.overlap.finder(episodes_r2)$overlap)
#sum(episodes.overlap.finder(episodes_r3)$overlap)
sum(episodes.overlap.finder(episodes_r4)$overlap)
#sum(episodes.overlap.finder(episodes_r5)$overlap)

```

```{r}
# 8 merge patient outcome data to episodes
episodes_r1<- add.stamm.new(episodes_r1,stamm.up)
episodes_r2<- add.stamm.new(episodes_r2,stamm.up)
#episodes_r3<- add.stamm.new(episodes_r3,stamm.up)
episodes_r4<- add.stamm.new(episodes_r4,stamm.up)
#episodes_r5<- add.stamm.new(episodes_r5,stamm.up)

#create full data episode data frames
rules<- c(1)
ticker<- 0
for(i in rules){#right now, only four decision rules are available
  im<- add.dataset(get(paste0("episodes_r",i)),diag.up_2,"diagnoses")
  ticker<- ticker+1
  print(ticker)
  # im<- add.dataset(im,impf.up,"impf")
  # ticker<- ticker+1
  # print(ticker)
  im<- add.dataset(im,labor.up,"lab")
  ticker<- ticker+1
  print(ticker)
  im<- add.dataset(im,lu.up,"lu")
  ticker<- ticker+1
  print(ticker)
  # im<- add.dataset(im,pzn.up_2,"pzn")
  # ticker<- ticker+1
  # print(ticker)
  im<- add.dataset(im,ueberweis.up,"ueberweis")
  ticker<- ticker+1
  print(ticker)

  assign(paste0("full.data.episodes_r",i),im)
}
rm(im)

```

```{r}
add.dataset.new<- function(episodedf, adddata, no.splits, no.cores, suffix){
  patients.episodedf<- levels(as.factor(as.character(episodedf$uniPatID)))
  preselector<- as.character(adddata$uniPatID) %in% patients.episodedf
  im<- adddata[preselector,]
  im<- chunk.data(im,no.splits)
  
  distinct.environment<- environment()
  adddata.cluster<- makeCluster(no.cores)
  clusterExport(adddata.cluster, varlist = c("im"), envir = distinct.environment)
  result.list<- parSapply(adddata.cluster,seq(1,no.splits),function(i){
    new.data<- im[[i]]
    entry.match<- numeric(nrow(new.data))
    for(i in seq_along(entry.match)){
      pat<- episodedf$uniPatID==new.data$uniPatID[i]
      start.check<- episodedf$start_date<=new.data$TG_DateNum
      end.check<- episodedf$end_date>=new.data$TG_DateNum
      entry.match[i]<- which(pat&start.check&end.check)
    }
    return(entry.match)
  })
  out<- cbind(episodedf,as.data.frame(matrix(NA,nrow = nrow(episodedf), ncol = ncol(adddata)-2)))
  col.selector<- colnames(adddata)!= "uniPatID" & colnames(adddata)!= "TG_DateNum"
  for(i in seq(1,no.splits)){
    for (j in seq(1,length(result.list[[i]]))) {
      if(result.list[[i]][j]!=0){
        out[,4:ncol(out)]<- im[[i]][j,col.selector]
      }
    }
  }
  return(out)
}
dataset.addition<- function(episodedf, df, no.splits, no.cores, suffix){
  episode.dl<- chunk.data(episodedf,no.splits)
  adddata.dl<- chunk.addata(episode.dl,df)
  
  suffix<- suffix
  dinstinct.environment<- environment()
  add.cluster<- makeCluster(no.cores)
  clusterExport(add.cluster,c("episode.dl","adddata.dl", "suffix"),distinct.environment)
  result.list<- parSapply(add.cluster,1:no.splits, function(j){
    n<- nrow(episode.dl[[j]])
    p<- nrow(adddata.dl[[1]])
    no.matches<- numeric(n)
    
    df_1<- episode.dl[[j]]|>
      arrange(uniPatID)
    addition<- as.data.frame(matrix(NA,nrow = n, ncol = 2*p-4))
    
    pat<- df_1$uniPatID[1]
    df_2<- adddata.dl[[j]]|>
      filter(uniPatID==pat)|>
      arrange(TG_DateNum)
    selector<- which(df_2$TG_DateNum >= df_1$start_date[1] & df_2$TG_DateNum >= df_1$end_date[1])
    if(length(selector)>=1){
      addition[1,seq(1,p-2)]<- df_2[min(selector),]|>
        select(-uniPatID,-TG_DateNum)
      addition[p-1,ncol(addition)]<- df_2[max(selector),]|>
        select(-uniPatID,-TG_DateNum)
      no.matches[1]<- length(selector)
    }
    
    for(i in seq(2,n)){
      if(df_1$uniPatID[i]!=df_1$uniPatID[i-1]){
        pat<- df_1$uniPatID[i]
        df_2<- adddata.dl[[j]]|>
          filter(uniPatID==pat)|>
          arrange(TG_DateNum)
      }
      selector<- which(df_2$TG_DateNum >= df_1$start_date[i] & df_2$TG_DateNum >= df_1$end_date[i])
      if(length(selector)>=1){
        addition[1,seq(1,p-2)]<- df_2[min(selector),]|>
          select(-uniPatID,-TG_DateNum)
        addition[p-1,ncol(addition)]<- df_2[max(selector),]|>
          select(-uniPatID,-TG_DateNum)
        no.matches[i]<- length(selector)
      }
    }
    out<- cbind(df_1,addition,no.matches)
    add.colnames<- colnames(adddata.dl[[1]])
    add.colnames<- add.colnames[add.colnames!= "uniPatID" & add.colnames!= "TG_DateNum"]
    colnames(out)<- c(colnames(df_1),
                      paste0("first", add.colnames),
                      paste0("last", add.colnames),
                      paste0("no.matches_",suffix))
    return(out)
  })
  
  stopCluster(add.cluster)
  return(result.list)
}
```

```{r}
chunk.adddata<- function(chunkeddl, adddata){
  l<- length(chunkeddl)
  chunked.adddata<- list()
  for(i in seq(1,l)){
    ids<- as.character(chunkeddl[[i]]$uniPatID)
    chunked.adddata[[i]]<- adddata|>
      filter(uniPatID %in% ids)
  }
  return(chunked.adddata)
}
```


```{r}
# 9 extract summary statistics
summary.stats<- function(episodedf){
  no.patients<- length(levels(as.factor(episodedf$uniPatID)))
  no.episodes<- nrow(episodedf)
  numbers<- list(
    no.episodes= nrow(episodedf),
    no.patients= length(levels(as.factor(episodedf$uniPatID))),
    no.stammdata.there= sum(episodedf$stamm_is_there, na.rm = TRUE),
    earliest.recorded.cough= TG_DateNum2date(min(episodedf$start_date)),
    latest.recorded.cough= TG_DateNum2date(max(episodedf$start_date)),
    no.males=sum(episodedf$Maennl, na.rm = TRUE),
    no.females=sum(episodedf$Weibl, na.rm = TRUE),
    no.transgender=sum(episodedf$Transgen, na.rm = TRUE),
    no.undefined.sex=sum(episodedf$Geschlechtundef, na.rm = TRUE),
    
    average.no.visit.per.patient=nrow(episodedf)/no.patients,
    percentage.stammdata.there= sum(episodedf$stamm_is_there, na.rm = TRUE)/no.episodes,
    percentage.males=sum(episodedf$Maennl, na.rm = TRUE)/no.episodes,
    percentage.females=sum(episodedf$Weibl, na.rm = TRUE)/no.episodes,
    percentage.transgender=sum(episodedf$Transgen, na.rm = TRUE)/no.episodes,
    percentage.undefined.sex=sum(episodedf$Geschlechtundef, na.rm = TRUE)/no.episodes,
    percentage.private.insurance= mean(episodedf$PKV, na.rm= TRUE),
    percentageretired= mean(episodedf$Status_R, na.rm= TRUE)
  )
  return(numbers)
}

```

```{r}
# 10 data discovery tool
diag.parameters<-list(
  initial.or.last= "last"
)
escalation.parameters<- list(
  type= 1
  #type: 1= blood test for Kreatinin, 2= referral to specialist care (pulmonologist, radiologist, hospital), 3= referral to pulmonologist, 4= referral to radiologist, 5= referral to hospital
)
constraints_1<- list(
  ""
)

escalation.parameters<- list(
  type= 1
  #type: 1= blood test for Kreatinin, 2= referral to specialist care (pulmonologist, radiologist, hospital), 3= referral to pulmonologist, 4= referral to radiologist, 5= referral to hospital
)
discovery.tool(1,dependent.variable = "escalation", research.question = "How much time elapsed between the initial cough and a Kreatinin test")
escalation.parameters<- list(
  type= 2
  #type: 1= blood test for Kreatinin, 2= referral to specialist care (pulmonologist, radiologist, hospital), 3= referral to pulmonologist, 4= referral to radiologist, 5= referral to hospital
)
discovery.tool(1,dependent.variable = "escalation", research.question = "How much time elapsed before the GP sent the patient to a specialist")
escalation.parameters<- list(
  type= 3
  #type: 1= blood test for Kreatinin, 2= referral to specialist care (pulmonologist, radiologist, hospital), 3= referral to pulmonologist, 4= referral to radiologist, 5= referral to hospital
)
discovery.tool(1,dependent.variable = "escalation", research.question = "How much time elapsed before the GP sent the patient to a pulmonologist")
escalation.parameters<- list(
  type= 4
  #type: 1= blood test for Kreatinin, 2= referral to specialist care (pulmonologist, radiologist, hospital), 3= referral to pulmonologist, 4= referral to radiologist, 5= referral to hospital
)
discovery.tool(1,dependent.variable = "escalation", research.question = "How much time elapsed before the GP sent the patient to a radiologist")
escalation.parameters<- list(
  type= 5
  #type: 1= blood test for Kreatinin, 2= referral to specialist care (pulmonologist, radiologist, hospital), 3= referral to pulmonologist, 4= referral to radiologist, 5= referral to hospital
)
discovery.tool(1,dependent.variable = "escalation", research.question = "How much time elapsed before the GP sent the patient to the hospital")
```



```{r}
summary.stats(episodedf = episodes_r1_stamm)
summary.stats(episodedf = episodes_r2_stamm)
```
```{r}
summary.plots(full.data.episodes_r1)
```

```{r}
#new stats and plots for Steinhäuser
pkv.summaries<- list()
pkv.summaries[[1]]<- summmary(stamm.up$PKV)
ticker<-2
clinic.ids<- levels(as.factor(stamm.up$PraxisID))
for(i in seq_along(clinic.ids)){
  pkv.summaries[[ticker]]<- summary(stamm.up$PKV[stamm.up$PraxisID==clinic.ids[i]])
}
pkv.summaries
#for overview, add data on the location of the clinic




```
```{r}
dl<- chunk.data(Stamm3,50)
check.cl<- makeCluster(4)
dist.env<- environment()
clusterExport(check.cl,varlist=list(dl),envir=dist.env)
res<- parSapply(check.cl,1:50,function(j){
  l<- levels(as.factor(dl[[j]]$uniPatID))
  id.collector<- numeric(length(l))
  for(i in seq_along(l)){
    id<- l[i]
    loc<- which(dl[[j]]$uniPatID==id)
    if(length(unique(dl[[j]]$Geburtsjahr[loc]))!=1 | length(unique(dl[[j]]$Geburtsmonat[loc]))!=1){
      id.collector[i]<- 1
    }
  }
})

```
```{r}
res<- sapply(1:50,function(j){
  l<- levels(as.factor(dl[[j]]$uniPatID))
  id.collector<- numeric(length(l))
  for(i in seq_along(l)){
    id<- l[i]
    loc<- which(dl[[j]]$uniPatID==id)
    if(length(unique(dl[[j]]$Geburtsjahr[loc]))!=1 | length(unique(dl[[j]]$Geburtsmonat[loc]))!=1){
      id.collector[i]<- 1
    }
  }
})
```
```{r}
df<- Stamm3|>
  arrange(uniPatID)
error.vec.year<- numeric(nrow(df))
error.vec.month<- numeric(nrow(df))
for(i in seq_along(error.vec.year)[-1]){
  if(df$uniPatID[i]==df$uniPatID[i-1]){
    if(!is.na(df$Geburtsjahr[i] & !is.na(df$Geburtsmonat[i]))){
      if(df$Geburtsjahr[i]!=df$Geburtsjahr[i-1]){
        error.vec.year[i]<- 1
      }
      if(df$Geburtsmonat[i]!=df$Geburtsmonat[i-1]){
        error.vec.month[i]<- 1
      }
    }
  }
}
id<- df$uniPatID[-1]
id_lag<- df$uniPatID[-nrow(df)]
na.rmvr<- !is.na(df$Geburtsjahr[-1]) & !is.na(df$Geburtsmonat[-nrow(df)])
yrs<- df$Geburtsjahr[-1]!=df$Geburtsjahr[-nrow(df)]
mnths<- df$Geburtsmonat[-1]!=df$Geburtsmonat[-nrow(df)]
error.vec.year<- as.numeric(id==id_lag & na.rmvr & yrs)
error.vec.month<- as.numeric(id==id_lag & na.rmvr & mnths)
```

```{r}
#list of diseases by icd-10 code
decision.rules<- c(1)
icd10.codes.3<- c()
for(i in decision.rules){
  im<- get(paste0("full.data.episodes_r",i))
  im<- as.vector(as.matrix(im[,grepl("icd10",colnames(im))]))
  im<- im[!is.na(im)]
  im<- im[im!="0"]
  icd10.codes.3<- c(icd10.codes.3,substr(im,1,3),substr(im,1,3))
}
icd10.codes.3<- levels(as.factor(icd10.codes.3))
all.diagnosed.bocks<- icd10.to.block(icd10.codes.3)
icd10_3digit_description.function<- function(dv){
  out<- numeric(length = length(dv))
  for(i in seq_along(dv)){
    out[i]<- icd10_description$text[which(dv[i]==icd10_description$code)]
  }
  return(out)
}
all.diagnosed.diseases<- data.frame(
  ICD10= icd10.codes.3,
  ICD10_description= icd10_description[match(icd10.codes.3,icd10_description[,1]),2],
  Gruppe= all.diagnosed.bocks,
  Kapitel= icd10.to.chapter(icd10.codes.3)
)
View(all.diagnosed.diseases)

```

```{r}
#dataset creating fun
full.episode.creator<- function(length.of.episode,decision.rule){
  im<- episode.fun.new(ipc.up_2,length.of.episode)
  
}
```






