---
title: "25.10.23"
author: "Raphael Kroes"
date: "2023-10-25"
output: html_document
---

Procedure:
1. Clear work space & load packages
2. Read in all functions (external functions.R file)
3. Read in data
4. Preprocessing I: create correct columns
5. Check whether multiple entries for the same date/ patient are in the data sets
6. Preprocessing II: Deal with multiple entries
7. Create list of data frames
8. Merge data sets
```{r}
# 1-2
rm(list=ls())
library(readxl)
library(dplyr)
library(parallel)
library(lubridate)
library(ggplot2)
# now read in all functions from functions.R file (CTRL+A, CTRL+Enter)
```

```{r}
# 3
# Read in data
setwd("N:/StudentischeHilfskraefte/_Kroes (Christoph)/Routinedaten/01_Husten/DB")

names.vec<- c("Diag3","Impf3","IPC23","Labor3","LU3","PZN3","Stamm3","Ueberweis3")


for (i in seq(1,length(names.vec))) {
  file.name<- paste0("DB_",names.vec[i],"_v03",".csv")
  im.file<- read.csv(file = file.name, header = TRUE, sep = ";")

  assign(names.vec[i],im.file)

}
# remove duplicate file and unnecessary name
rm(file.name,im.file)

ListeKrankenkassen<- read.csv(file = "ListeKrankenkassen.csv", header = TRUE, sep = ";")
altersstruktur_deutschland <- read_excel("altersstruktur deutschland.xlsx")

```

```{r}
# 4
diag.up<- Diag3 |> 
  select(uniPatID,TG_DateNum,DiagTyp,icd10)|>
  distinct()
diag.up$uniPatID<- as.factor(diag.up$uniPatID)
diag.up$DiagTyp<- as.factor(diag.up$DiagTyp)

impf.up<- Impf3|> 
  select(uniPatID,TG_DateNum,Influenza,starts_with("Cov"))|>
  distinct()
impf.up$uniPatID<- as.factor(impf.up$uniPatID)

ipc.up<- IPC23 |>
  select(uniPatID,TG_DateNum,AnamnTyp,ipc2)
ipc.up$uniPatID<- as.factor(ipc.up$uniPatID)
ipc.up$AnamnTyp<- as.factor(ipc.up$AnamnTyp)

labor.up<- Labor3|>
  select(uniPatID,TG_DateNum,Untersuchung,Wertnum,NormLB,NormUB) |>
  filter(Untersuchung=="KREA")
labor.up$KREA_unter<- as.numeric(labor.up$Wertnum<labor.up$NormLB)
labor.up$KREA_ueber<- as.numeric(labor.up$Wertnum>labor.up$NormUB)
labor.up<- labor.up|>
  select(uniPatID,TG_DateNum,KREA_unter,KREA_ueber)|>
  distinct()
labor.up$uniPatID<- as.factor(labor.up$uniPatID)

lu.up<- LU3|> 
  select(uniPatID,TG_DateNum)|>
  distinct()
lu.up$lu.dummy<- 1
lu.up$uniPatID<- as.factor(lu.up$uniPatID)

pzn.up<- PZN3 |> 
  select(uniPatID,TG_DateNum,PZN) |> 
  filter(TG_DateNum>0)|>
  distinct()
pzn.up$uniPatID<- as.factor(pzn.up$uniPatID)
pzn.up$PZN<- as.factor(pzn.up$PZN)

stamm.up<- Stamm3
stamm.up$PKV<- IK2PKV(stamm.up$IK)
stamm.up<- stamm.up|> 
  filter(IK>0)|>
  select(-PatID,-index_i,-IK,-Kasse,-PLZ)|>
  distinct()|>
  arrange(uniPatID,desc(TG_DateNum))
stamm.up$uniPatID<- as.factor(stamm.up$uniPatID)

ueberweis.up<- Ueberweis3|>
  select(uniPatID,TG_DateNum,Uberw_Pneumo,Uberw_Radiol,Uberw_KH) |>
  filter(Uberw_Pneumo>0|Uberw_Radiol>0|Uberw_KH>0)|>
  distinct()
ueberweis.up$uniPatID<- as.factor(ueberweis.up$uniPatID)
```
```{r}
#free up memory by clearing the original, raw datasets out
rm(list = names.vec)
```

```{r}
# 5
contains.multiple.entries(diag.up)
contains.multiple.entries(impf.up)
contains.multiple.entries(ipc.up)
contains.multiple.entries(labor.up)
contains.multiple.entries(lu.up)
contains.multiple.entries(pzn.up)
contains.multiple.entries(stamm.up)
contains.multiple.entries(ueberweis.up)

```

STOP: the difference between number of rows and patient/ time combinations must be 0. We believe diag.up, ipc.up, and pzn.up have multiple entries by design. We believe impf.up, labor.up, stamm.up, and ueberweis.up should have only one line per patient/ time combination. In #6.1 we remedy the presumed errors by selecting the last entry for each patient/ time combination. In #6.2 we write the multiple data points of diag.up, ipc.up, and pzn.up in additional columns. Both procedures leave us with unique date/ time combinations for each data set.
In #6.2, we do not keep all entries for diag.up and ipc.up. There are a few entreis with unreasonably high numbers of diagnoses or symptoms. Therefore, we truncate the number observations at the 95% quantile of the distribution of entries per combination. If the last sentence is not clear in meaning, please run the commented code to gain better insight.
```{r}
# 6.1
impf.up<- data.repair(impf.up)
contains.multiple.entries(impf.up)

labor.up<- data.repair(labor.up)
contains.multiple.entries(labor.up)

stamm.up<- data.repair(stamm.up)
contains.multiple.entries(stamm.up)

ueberweis.up<- data.repair(ueberweis.up)
contains.multiple.entries(ueberweis.up)

```
```{r}
# 6.2
x_diag<- quantile(table(paste(diag.up$uniPatID,diag.up$TG_DateNum)), probs= 0.95)
x_ipc<- quantile(table(paste(ipc.up$uniPatID,ipc.up$TG_DateNum)), probs= 0.95)
x_pzn<- quantile(table(paste(pzn.up$uniPatID,pzn.up$TG_DateNum)), probs= 1)

# table(paste0(diag.up$uniPatID,diag.up$TG_DateNum)
# quantile(table(paste0(diag.up$uniPatID,diag.up$TG_DateNum)))

tic()
diag.up_2<- aligner.parallel(diag.up, x_diag, no.splits=12)
contains.multiple.entries(diag.up)
toc()

ipc.up_2<- aligner(ipc.up, x_ipc)
contains.multiple.entries(ipc.up)

pzn.up_2<- aligner(pzn.up, x_pzn)
contains.multiple.entries(pzn.up)
```

```{r}
# no.14
aligner<- function(df,x, debugging=FALSE){
  #finds rows with non-unique uniPatID/ TG_DateNum combinations and writes them all into one row. x specifies the maximum number of rows from df that are framed into a single row in the output data frame. If more than x rows are found in the data set, the first x rows are kept and the other ones are discarded.
  raw.combinations<- paste0(df$uniPatID,df$TG_DateNum)
  combinations<- levels(as.factor(raw.combinations))
  l<- length(combinations)
  memory<- data.frame(a=combinations, b= NA, c=NA)
  #memory<- matrix(c(combinations,rep(NA,2*l)),ncol = 3)
  colnames(memory)<- c("combination","no. seen before","last seen in row")
  
  out<- as.data.frame(matrix(0, nrow = l, ncol = 2+x*(ncol(df)-2)))
  
  ticker<- 1 #answer to "Onto which row in out do we write right now?"
  
  partial.row<- colnames(df)!= "uniPatID" & colnames(df)!= "TG_DateNum"
  colnames(out)<- c(colnames(df),paste(rep(colnames(df)[partial.row],x-1),sort(rep(1:(x-1),ncol(df)-2)),sep = "_"))
  
  progress.bar<- txtProgressBar(min = 0, max = l, initial = 0) 
  
  for(i in seq(1,nrow(df))){
    setTxtProgressBar(progress.bar,i)
    case<- raw.combinations[i]
    location<- which(combinations==case)
                      
    if(is.na(memory[location,2])){
      out[ticker,1:ncol(df)]<- df[i,]
      memory[location,2]<- 1
      memory[location,3]<- ticker
      ticker<- ticker+1
    }else{
      no.seen<- memory[location,2]
      if(no.seen<x){
        last.seen<- memory[location,3]
        sel.col<-seq(1,ncol(df)-2)+no.seen*(ncol(df)-2)+2
        sel.data<- df[i,partial.row]
        #browser()
        out[last.seen,sel.col]<- sel.data
        memory[location,2]<- memory[location,2]+1
      }

    }
  }
  close(progress.bar)
  if(debugging==TRUE){
    return(list(as.data.frame(out),memory))
  }else{
    return(as.data.frame(out))
  }
}

aligner.parallel<- function(df, x, no.splits, no.cores=detectCores()-1){
  chunked.df<- chunk.data(df, no.splits)
  align.cluster<- makeCluster(no.cores)
  distinct_env<- environment()
  clusterExport(cl = align.cluster, varlist = c("chunked.df","aligner","x"), envir = distinct_env)
  result.list<- parSapply(cl = align.cluster, seq_along(chunked.df), FUN = function(i){
    df_i<- chunked.df[[i]]
    return(aligner(chunked.df,x))
  })
  stopCluster(align.cluster)
  browser()
  out<- sapply(result.list,rbind)
  return(out)
}
```




```{r}
# For some reason, some of the dates were changed from their original numeric class to the character class. This chunk remedies this error.
diag.up_2$TG_DateNum<- as.numeric(diag.up_2$TG_DateNum)
ipc.up_2$TG_DateNum<- as.numeric((ipc.up_2$TG_DateNum))
```

```{r}
#create episodes based on the data
episodes<- episode.fun(ipc.up_2,56)
```

There must be no overlap in the timing of the episodes in order to map diagnoses and treatments to the episodes.
There is no decision rule we can enforce that distinguishes perfectly whether episodes match or match not. Therefore, we implement different decision rules.

```{r}
#decision rule 1: If the timing of episodes overlaps, we treat them as one episode
#decision rule 2: If the timing of episodes overlaps, we treat them as two distinct episodes. The last day of the earlier episode is the day before the new episode begins.
#decision rule 3: For every episode, we select the end date as the earlier of the following two: (1) the previously selected maximum length of episode, (2) the next recorded symptom or batch of symptoms which is not cough (R05).
#decision rule 4: If the timing of episodes overlaps, we check whether there is a change in quarter between those two visits. If there is a change, we treat them as one and use the first incident's end date, otherwise we set the last day of the earlier episode to be last day of the quarter.
#decision rule 5: Combination of rules 3 and 4. If there is an overlap between episodes, we consider them as one if the quarter ends between the two records. However, if symptoms are recorded between these dates which are not cough, the first episode ends with the day before the new symptoms- even if the quarter ends between these days.


#check rule3: does it also cut off for dates before the overlapping time? Because it should by our rationale
#test for functionality/ troubleshoot
episodes.dr4<- function(episodedf){
  # Applies decision rule 5 to a raw (i.e. containing overlapping episodes) episode data frame.
  earliest.TG_Date<- min(episodedf$start_date)
  latest.TG_Date<- max(episodedf$start_date)
  earliest.year.POSIXlt<- year(TG_DateNum2date(earliest.TG_Date))
  latest.year.POSIXlt<- year(TG_DateNum2date(latest.TG_Date))
  no.years<- latest.year.POSIXlt-earliest.year.POSIXlt
  threshold.dates<- numeric(4*no.years)
  for(i in seq(1,no.years)){
    threshold.dates[1+(i-1)*4]<- paste0(seq(earliest.year.POSIXlt, latest.year.POSIXlt)[i], "-01-01")
    threshold.dates[2+(i-1)*4]<- paste0(seq(earliest.year.POSIXlt, latest.year.POSIXlt)[i], "-04-01")
    threshold.dates[3+(i-1)*4]<- paste0(seq(earliest.year.POSIXlt, latest.year.POSIXlt)[i], "-07-01")
    threshold.dates[4+(i-1)*4]<- paste0(seq(earliest.year.POSIXlt, latest.year.POSIXlt)[i], "-10-01")
  }
  threshold.dates_num<- as.numeric(as.Date(threshold.dates, origin= "0000-01-01"))
  #if(all(as.Date(threshold.dates_num!=as.Date(threshold.dates)))) stop("Conversion error in the threshold date!")
  
  n<- nrow(episodedf)
  out<- episodedf
  for(i in seq(2,n)){
    if(episodedf$uniPatID[i]==episodedf$uniPatID[i-1]){
      if(out$start_date[i]<out$end_date[i-1]){
        if(sum(out$start_date[i]>threshold.dates_num & out$end_date[i-1]<threshold.dates_num)==1){#condition: one threshold numeric date lies between these two
          outf$start_date[i]<- out$start_date[i-1]
          out$end_date[i]<- out$end_date[i-1]
        }else if(sum(out$start_date[i]>threshold.dates_num & out$end_date[i-1]<threshold.dates_num)>1){
          warning(paste("Between the coughing incidents, lies more than one quarter. To check out the episode, have a look at lines", (i-1),"&", i, "in the original dataset (episodedf, not the output dataset)."))
          outf$start_date[i]<- out$start_date[i-1]
          out$end_date[i]<- out$end_date[i-1]
        }else{
          out$end_date[i-1]<- out$start_date[i]-1
      }
    }
    }
    
  }
  out<- distinct(out)
  return(out)
}
episodes_r4<- episodes.dr4(episodes)
a<-episodes.dr4(episodedf = episodes)

#work in progress
episodes.dr5<- function(episodedf,ipc, debug=FALSE){
  # Applies decision rule 5 to a raw (i.e. containing overlapping episodes) episode data frame.
  patients<- levels(as.factor(episodedf$uniPatID))
  next.incident<- numeric(nrow(episodedf))
  for(i in seq(1,length(patients))){
    pat_i<- patients[i]
    rows.episodes<- which(episodedf$uniPatID==pat_i)
    start.dates.episodes<- episodedf$start_date[rows.episodes]
    end.dates.episodes<- episodedf$end_date[rows.episodes]
    incident.dates<- ipc$TG_DateNum[ipc$uniPatID==pat_i]
    store<- numeric(length(start.dates.episodes))
    for(j in seq(1, length(start.dates.episodes))){
      indices<- which(incident.dates> start.dates.episodes[j] & incident.dates<end.dates.episodes[j])
      if(length(indices)>0){
        store[j]<- min(incident.dates[indices])
      }else{
        store[j]<- end.dates.episodes[j]
      }
    }
    next.incident[rows.episodes]<- store
  }
  
  if(debug==TRUE){
    out<- cbind(episodedf,next.incident)
  }else{
    out<- episodedf
    out$end_date<- next.incident
  }
  return(out)
}

episodes.overlap.finder<- function(episodedf, date=FALSE){
  n<- nrow(episodedf)
  overlap<- numeric(n)
  for(i in seq(2,n)){
    if(episodedf$uniPatID[i]==episodedf$uniPatID[i-1]){
      if(episodedf$start_date[i]<episodedf$end_date[i-1]){
        overlap[i]<- 1
      }
    }
  }
  out<- episodedf
  out$overlap<- overlap
  if(date==TRUE){
    out$start_date<- TG_DateNum2date(out$start_date)
    out$end_date<- TG_DateNum2date(out$end_date)
  }
  return(out)
}
```
```{r}
episodes_r1<- episodes.dr1(episodes)
episodes_r2<- episodes.dr2(episodes)
episodes_r3<- episodes.dr3(episodes,ipc.up_2,TRUE)
episodes_r4<- episodes.dr4(episodes)

episodes.overlap<- episodes.overlap.finder(episodes)
sum(episodes.overlap.finder(episodes)$overlap)

sum(episodes.overlap.finder(episodes_r1)$overlap)
sum(episodes.overlap.finder(episodes_r2)$overlap)
sum(episodes.overlap.finder(episodes_r3)$overlap)
sum(episodes.overlap.finder(episodes_r4)$overlap)


episodes_r1_2<- episodes.dr1(episodes.dr1(episodes.dr1(episodes_r1)))
episodes_r1_2_o<- episodes.overlap.finder(episodes_r1_2)
sum(episodes.overlap.finder(episodes_r1_2_o)$overlap)

#debug here!!!
episodes.dr1<- function(episodedf, no.it, debug=FALSE){
  # Applies decision rule 1 to a raw (i.e. containing overlapping episodes) episode data frame. Relies on episodes.overlap.finder
  out<- episodedf
  #out<- episodes.overlap.finder(out)
  ticker<- 1
  while(ticker<=no.it){
    n<- nrow(out)
    for(i in seq(2,n)){
      if(episodedf$uniPatID[i]==episodedf$uniPatID[i-1]){
        if(episodedf$end_date[i-1]>episodedf$start_date[i]){
          #create duplicate episodes, then remove the duplicates
          out$start_date[i]<- out$start_date[i-1]
          out$end_date[i-1]<- out$end_date[i]
        }
      }
    }
    out<- distinct(out)
    ticker<- ticker+1
  }
  
  if(debug==TRUE){
    out<- episodes.overlap.finder(out)
    overlap.exists<- sum(out$overlap)>0
    out<- list(out, overlap.exists)
  }
  return(out)
}

episodes.dr1<- function(episodedf, length.of.episode){
  out<- episodedf
  out$uniPatID<- as.factor(as.character(out$uniPatID))
  n<- nrow(out)
  for(i in seq(2,n)){
    if(out$uniPatID[i]==out$uniPatID[i-1]){
      if((out$start_date[i-1]+length.of.episode)>out$start_date[i]){
        out$start_date[i]<- out$start_date[i-1]
        out$end_date[i-1]<- out$end_date[i]
      }
    }
  }
}
episodes.dr1<- function(episodedf){
  library(dplyr)
  n<- nrow(episodedf)
  out<- episodedf|>
    arrange(uniPatID,start_date)
  patients<- out$uniPatID
  compare_1<- patients[1:(n-1)]==patients[2:n]
  compare_2<- out$start_date[2:n]<=out$end_date[1:(n-1)]
  joint.comp<- compare_1 & compare_2
  for(i in seq_along(joint.comp)){
    if(joint.comp[i]==TRUE){
      out$start_date[i+1]<- out$start_date[i]
      out$end_date[i]<- out$end_date[i+1]
    }
  }
  out<- distinct(out)
  return(out)
}

episodes.dr1<- function(episodedf){
  length.of.episode<- episodedf$end_date[1]-episodedf$start_date[1]
  patients<- levels(as.factor(as.character(out$uniPatID)))
  out.list<- list()
  for(i in seq_along(patients)){
    pat_i<- patients[i]
    dates<- sort(episodedf$start_date[episodedf$uniPatID==pat_i])
    l<- length(dates)
    merge.choice<- diff(dates)>length.of.episode
    episode.matrix<- matrix(NA,nrow = 1+!merge.choice, ncol = 2)
    episode.matrix[1,1]<- dates[1]
    ticker<- 1
    for(j in seq_along(merge.choice)){
      if(merge.choice[j]){
        episode.matrix[ticker,2]<- dates[1+j]+length.of.episode
      }else{
        ticker<- ticker+1
        episode.matrix[ticker,1]<- dates[1+j]
        episode.matrix[ticker,1]<- dates[1+j]+length.of.episode
    }
  }
  out.list[[i]]<- cbind(rep(pat_i,nrow(episode.matrix)),episode.matrix)
  }
  out<- as.data.frame(sapply(out.list,rbind))
  colnames(out)<- c("uniPatID","start_date","end_date")
  return(out)
}
episodes_r1_3<- episodes.dr1(episodes)
x<- episodes.overlap.finder(episodes_r1_3)
sum(x$overlap)

merge_overlapping_intervals <- function(episodedf) {
  episodedf <- episodedf[order(episodedf$uniPatID, episodedf$start_date), ]
  episodedf$group <- cumsum(c(1, diff(episodedf$start_date) > 0))
  merged_df <- aggregate(cbind(start_date = start_date, end_date = end_date) ~ uniPatID + group, data = episodedf, FUN = range)
  merged_df$group <- NULL
  return(merged_df)
}
x<- merge_overlapping_intervals(episodes)
y<- episodes.overlap.finder(x)
sum(y$overlap)

episodes_r1_3<- episodes.dr1(episodes,50,TRUE)
sum(episodes_r1_3[[1]]$overlap)

x<- 1:20
y<- numeric(length(x))
for(i in seq_along(x)){
  episodes_r1_3<- episodes.dr1(episodes,i,TRUE)
  y[i]<- sum(episodes_r1_3[[1]]$overlap)
}

episodes_r1_3<- episodes.overlap.finder(episodes_r1_3)
```




```{r}
add.dataset<- function(episodedf, adddata,name.dataset){
  #matches the entries from any suitable dataset to the ones from an episode data frame.
  #episodedf is the episode data frame, as produced by episodes.drx
  #adddata is any of the cleaned and prepared datasets except for Stammdaten
  #name.dataset is a character string to name the number of matches variable.
  #The function returns an episode data frame with the first and last matches of the added dataset, and the number of entries in adddata that are a match for this episode.
  patients<- levels(as.factor(as.character(episodedf$uniPatID)))
  adddata$uniPatID<- as.character(adddata$uniPatID)
  n<- nrow(episodedf)
  no.matches<- numeric(n)
  first.match<- as.data.frame(matrix(NA,nrow = n, ncol = ncol(adddata)))
  last.match<- as.data.frame(matrix(NA,nrow = n, ncol = ncol(adddata)))
  for(j in seq_along(patients)){
    pat_i<- patients[j]
    rows_episode<- which(episodedf$uniPatID==pat_i)
    match.data<- adddata|>
      filter(uniPatID==pat_i)|>
      arrange(TG_DateNum)
    if(nrow(match.data)>0){
      for(i in seq_along(rows_episode)){
        sd<- episodedf$start_date[rows_episode[i]]
        ed<- episodedf$end_date[rows_episode[i]]
        matches<- which(match.data$TG_DateNum>=sd & match.data$TG_DateNum<=ed)
        if(length(matches)>0){
          no.matches[rows_episode[i]]<- length(matches)
          first.match[rows_episode[i],]<- match.data[min(matches),]
          last.match[rows_episode[i],]<- match.data[max(matches),]
        }
      }
    }
  }
  colnames(first.match)<- paste0("first_",colnames(adddata))
  colnames(last.match)<- paste0("last_",colnames(adddata))
  col.selector<- colnames(adddata)!= "uniPatID" & colnames(adddata)!= "TG_DateNum"
  out<- cbind(episodedf, first.match[,col.selector],last.match[,col.selector],no.matches)
  colnames(out)[ncol(out)]<- paste0("no.matches_",name.dataset)
  return(out)
}

```

```{r}
#add stammdata


add.stamm<- function(episodedf, stamm){
  #adds stamm data to the episode data frame by matching entries.
  #episodedf is a data frame created through one of the decision rules episodes.drx
  #stamm is a cleaned and prepared stamm data frame (e.g. stamm.up_2)
  #The function returns an episode data frame with the Stamm data matched to the episodes. There is also a variable called stamm_is_there, which is 1 if a Stamm entry was able to be matched, and 0 if no Stamm entry was able to be matched to that patient/ episode.
  n<- nrow(episodedf)
  p<- ncol(episodedf)
  p_out<- p+ncol(stamm)
  out<- as.data.frame(matrix(NA, nrow = n, ncol = p_out))
  stamm$uniPatID<- as.character(stamm$uniPatID)
  stamm.is.there<- numeric(n)
  for(i in seq(1,n)){
    pat_i<- as.character(episodedf$uniPatID[i])
    pat.rows<- which(stamm$uniPatID==pat_i)
    if(length(pat.rows)>0){
      dates<- stamm$TG_DateNum[pat.rows]
      im<- dates<=episodedf$start_date[i]
      if(all(!im)){
        #if no Stamm data has been recorded prior to the first coughing (i.e. first visit of clinic), this might be due to the patient being at the clinic for the first time and the doctor back dated the start of coughing (i.e. first health incident, which occurred before the visit visit at the clinic).
        loc<- pat.rows[1]
      }else{
        loc<- pat.rows[sum(im)]
      }
      out[i,seq(p+1,p_out)]<- stamm[loc,]
      stamm.is.there[i]<- 1
    }
  }
  unipat.col<- p+which(colnames(stamm)=="uniPatID")
  #remove duplicate uniPatID column
  out<- out[,-(unipat.col)]
  out[,1:p]<- episodedf
  out<- cbind(out,stamm.is.there)
  colnames(out)<- c(colnames(episodedf),colnames(stamm),"stamm_is_there")[-unipat.col]
  stamm_date.col<- which(colnames(out)=="TG_DateNum")
  colnames(out)[stamm_date.col]<- "Stamm_date"
  return(as.data.frame(out))
}

```
```{r}
episodes_r1_stamm<- add.stamm(episodes_r1,stamm.up)
episodes_r2_stamm<- add.stamm(episodes_r2,stamm.up)
episodes_r3_stamm<- add.stamm(episodes_r3,stamm.up)
```
```{r}
#extract summary statistics
summary.stats<- function(episodedf){
  no.patients<- length(levels(as.factor(episodedf$uniPatID)))
  no.episodes<- nrow(episodedf)
  numbers<- list(
    no.episodes= nrow(episodedf),
    no.patients= length(levels(as.factor(episodedf$uniPatID))),
    no.stammdata.there= sum(episodedf$stamm_is_there, na.rm = TRUE),
    earliest.recorded.cough= TG_DateNum2date(min(episodedf$start_date)),
    latest.recorded.cough= TG_DateNum2date(max(episodedf$start_date)),
    no.males=sum(episodedf$Maennl, na.rm = TRUE),
    no.females=sum(episodedf$Weibl, na.rm = TRUE),
    no.transgender=sum(episodedf$Transgen, na.rm = TRUE),
    no.undefined.sex=sum(episodedf$Geschlechtundef, na.rm = TRUE),
    
    average.no.visit.per.patient=nrow(episodedf)/no.patients,
    percentage.stammdata.there= sum(episodedf$stamm_is_there, na.rm = TRUE)/no.episodes,
    percentage.males=sum(episodedf$Maennl, na.rm = TRUE)/no.episodes,
    percentage.females=sum(episodedf$Weibl, na.rm = TRUE)/no.episodes,
    percentage.transgender=sum(episodedf$Transgen, na.rm = TRUE)/no.episodes,
    percentage.undefined.sex=sum(episodedf$Geschlechtundef, na.rm = TRUE)/no.episodes,
    percentage.private.insurance= mean(episodedf$PKV, na.rm= TRUE),
    percentageretired= mean(episodedf$Status_R, na.rm= TRUE)
  )
  return(numbers)
}
summary.plots<- function(episodedf){
  earliest.TG_Date<- min(episodedf$start_date)
  latest.TG_Date<- max(episodedf$start_date)
  earliest.year.POSIXlt<- year(TG_DateNum2date(earliest.TG_Date))
  latest.year.POSIXlt<- year(TG_DateNum2date(latest.TG_Date))
  no.years<- latest.year.POSIXlt-earliest.year.POSIXlt
  pandemic.start<- date2TG_DateNum("2020-01-01")
  pandemic.end<- date2TG_DateNum("2023-01-01")
  #no visits
  x<- round(as.vector((table(episodedf$uniPatID)/no.years)),3)
  d<- as.data.frame(table(x))
  p<- ggplot(d, aes(x=x,y=Freq)) +
    geom_bar(stat = "identity", fill="skyblue") +
    labs(title = "How often did patients attend their GP?",x = "Number of visits per year", y= "Frequency")
  
  ggsave("no_visits.png", plot = p, path = getwd(), device = "png")
  browser()
  #age
  x<- as.numeric(year(TG_DateNum2date(episodedf$start_date)))-episodedf$Geburtsjahr
  max.age<- max(c(100,max(x)))
  d<- as.data.frame(table(x))
  d$Freq<- d$Freq/sum(d$Freq)
  d_copy<- data.frame(seq(1,max.age), numeric(max.age))
  colnames(d_copy)<- colnames(d)
  for(i in seq(1, nrow(d))){
    age<- d[i,1]
    freq<- d[i,2]
    d_copy[age,2]<- freq
  }
  d<- d_copy
  y<- age.weights(1,max.age)
  p<- ggplot(d, aes(x=x,y=Freq)) +
    geom_bar(stat = "identity", fill="skyblue") +
    geom_line(aes(y = y), color = "red") +
    scale_x_discrete(labels = function(z) ifelse(as.numeric(z) %% 10 ==0, as.character(z),"")) +
    labs(title = "How old were the patients who had cough?",x = "Age in years", y= "Frequency")
  ggsave("age.png", plot = p, path = getwd(), device = "png")
  
  #no. visits with/out pandemic
  before.pandemic<- episodedf[episodedf$start_date<pandemic.start,]
  only.pandemic<- episodedf[episodedf$start_date>=pandemic.start & episodedf$start_date<pandemic.end,]
  length.pandemic<- 3
  
  x<- round(as.vector((table(before.pandemic$uniPatID)/(no.years-length.pandemic))),3)#change to correct no of years, and make it annual
  d<- as.data.frame(table(x))
  p<- ggplot(d, aes(x=x,y=Freq)) +
    geom_bar(stat = "identity", fill="skyblue") +
    labs(title = "How often did patients attend their GP before the pandemic?",x = "Number of visits per year", y= "Frequency")
  
  ggsave("no_visits_before_pandemic.png", plot = p, path = getwd(), device = "png")
  
  x<- round(as.vector((table(only.pandemic$uniPatID)/no.years)),3)#change to correct no of years, and make it annual
  d<- as.data.frame(table(x))
  p<- ggplot(d, aes(x=x,y=Freq)) +
    geom_bar(stat = "identity", fill="skyblue") +
    labs(title = "How often did patients attend their GP during the pandemic?",x = "Number of visits per year", y= "Frequency")
  
  ggsave("no_visits_during_pandemic.png", plot = p, path = getwd(), device = "png")
}

summary.plots(episodes_r1_stamm)

x<- as.vector(table(episodes_r1_stamm$uniPatID))

table(as.vector(table(episodes_r1_stamm$uniPatID)))

barplot(table(as.vector(table(episodes_r1_stamm$uniPatID))))
d<- as.data.frame(table(x))
ggplot(d, aes(x=x,y=)) +
  geom_bar(stat = "identity", fill="skyblue") +
  labs(title = "plot w ggplot2",x = "x-axis", y= "Frequency")
```

```{r}
summary.stats(episodedf = episodes_r1_stamm)
summary.stats(episodedf = episodes_r2_stamm)
```
```{r}

```

```{r}
#new stats and plots for Steinhäuser
pkv.summaries<- list()
pkv.summaries[[1]]<- summmary(stamm.up$PKV)
ticker<-2
clinic.ids<- levels(as.factor(stamm.up$PraxisID))
for(i in seq_along(clinic.ids)){
  pkv.summaries[[ticker]]<- summary(stamm.up$PKV[stamm.up$PraxisID==clinic.ids[i]])
}
pkv.summaries
#for overview, add data on the location of the clinic




```
```{r}
date2TG_DateNum<- function(date) as.numeric(as.Date(date)) +719529
date2TG_DateNum("0000-01-01")
```
```{r}
age.weights<- function(startage,endage){
  
  if(startage<1) stop("By default, the start age has to be at least one year.")
  if(startage>85) stop("All ages are dropped due to the start age being too high. Please select a lower start age.")
  if(endage<1) stop("The end age is too low. It has to be no lower than one year.")
  if(endage>84) warning("Please note that the data provided by the statistical office is placed into a single bin from age 85 on. All ages from that bin are therefore treated as equally distributed across the range from 85 to the end date.")
  vector<- altersstruktur_deutschland[,2]
  if(endage<=84){
    out<- vector[seq(startage+1,endage+1)]
  }else{
    l<- endage-84
    im<- vector[seq(startage+1,85)]
    out<- c(im,rep(vector[86]/l,l))
  }
  out<- out/sum(out)
  return(out)
}
age.weights(1,100)
```

```{r}

```






