---
title: "14.09.23"
author: "Raphael Kroes"
date: "2023-09-14"
output: html_document
---

Procedure:
1. Clear work space & load packages
2. Read in all functions (external functions.R file)
3. Read in data
4. Preprocessing I: create correct columns
5. Check whether multiple entries for the same date/ patient are in the data sets
6. Preprocessing II: Deal with multiple entries
7. Create list of data frames
8. Merge data sets
```{r}
# 1-2
rm(list=ls())
library(dplyr)
library(parallel)
# now read in all functions from functions.R file (CTRL+A, CTRL+Enter)
```

```{r}
# 3
# Read in data
setwd("N:/StudentischeHilfskraefte/_Kroes (Christoph)/Routinedaten/01_Husten/DB")

names.vec<- c("Diag3","Impf3","IPC23","Labor3","LU3","PZN3","Stamm3","Ueberweis3")


for (i in seq(1,length(names.vec))) {
  file.name<- paste0("DB_",names.vec[i],"_v03",".csv")
  im.file<- read.csv(file = file.name, header = TRUE, sep = ";")

  assign(names.vec[i],im.file)

}
# remove duplicate file and unnecessary name
rm(file.name,im.file)

# adapt this part
ListeKrankenkassen<- read.csv(file = "ListeKrankenkassen.csv", header = TRUE, sep = ";")
```

```{r}
# 4
diag.up<- Diag3 |> 
  select(uniPatID,TG_DateNum,DiagTyp,icd10)|>
  distinct()

impf.up<- Impf3|> 
  select(uniPatID,TG_DateNum,Influenza,starts_with("Cov"))|>
  distinct()

ipc.up<- IPC23 |>
  select(uniPatID,TG_DateNum,AnamnTyp,ipc2)

labor.up<- Labor3|>
  select(uniPatID,TG_DateNum,Untersuchung,Wertnum,NormLB,NormUB) |>
  filter(Untersuchung=="KREA")
labor.up$KREA_unter<- as.numeric(labor.up$Wertnum<labor.up$NormLB)
labor.up$KREA_ueber<- as.numeric(labor.up$Wertnum>labor.up$NormUB)
labor.up<- labor.up|>
  select(uniPatID,TG_DateNum,KREA_unter,KREA_ueber)|>
  distinct()

lu.up<- LU3|> 
  select(uniPatID,TG_DateNum)|>
  distinct()
lu.up$lu.dummy<- 1

pzn.up<- PZN3 |> 
  select(uniPatID,TG_DateNum,PZN) |> 
  filter(TG_DateNum>0)|>
  distinct()

stamm.up<- Stamm3
stamm.up$PKV<- IK2PKV(stamm.up$IK)
stamm.up<- stamm.up|> 
  filter(IK>0)|>
  select(-PatID,-index_i,-IK,-Kasse,-PLZ)|>
  distinct()

ueberweis.up<- Ueberweis3|>
  select(uniPatID,TG_DateNum,Uberw_Pneumo,Uberw_Radiol,Uberw_KH) |>
  filter(Uberw_Pneumo>0|Uberw_Radiol>0|Uberw_KH>0)|>
  distinct()
```
```{r}
# 5
contains.multiple.entries(diag.up)
contains.multiple.entries(impf.up)
contains.multiple.entries(ipc.up)
contains.multiple.entries(labor.up)
contains.multiple.entries(lu.up)
contains.multiple.entries(pzn.up)
contains.multiple.entries(stamm.up)
contains.multiple.entries(ueberweis.up)

```

STOP: the difference between number of rows and patient/ time combinations must be 0. We believe diag.up, ipc.up, and pzn.up have multiple entries by design. We believe impf.up, labor.up, stamm.up, and ueberweis.up should have only one line per patient/ time combination. In #6.1 we remedy the presumed errors by selecting the last entry for each patient/ time combination. In #6.2 we write the multiple data points of diag.up, ipc.up, and pzn.up in additional columns. Both procedures leave us with unique date/ time combinations for each data set.
In #6.2, we do not keep all entries for diag.up and ipc.up. There are a few entreis with unreasonably high numbers of diagnoses or symptoms. Therefore, we truncate the number observations at the 95% quantile of the distribution of entries per combination. If the last sentence is not clear in meaning, please run the commented code to gain better insight.
```{r}
# 6.1
impf.up<- data.repair(impf.up)
contains.multiple.entries(impf.up)

labor.up<- data.repair(labor.up)
contains.multiple.entries(labor.up)

stamm.up<- data.repair(stamm.up)
contains.multiple.entries(stamm.up)

ueberweis.up<- data.repair(ueberweis.up)
contains.multiple.entries(ueberweis.up)

```
```{r}
# 6.2
x_diag<- quantile(table(paste0(diag.up$uniPatID,diag.up$TG_DateNum)), probs= 0.95)
x_ipc<- quantile(table(paste0(ipc.up$uniPatID,ipc.up$TG_DateNum)), probs= 0.95)
x_pzn<- quantile(table(paste0(pzn.up$uniPatID,pzn.up$TG_DateNum)), probs= 1)

# table(paste0(diag.up$uniPatID,diag.up$TG_DateNum)
# quantile(table(paste0(diag.up$uniPatID,diag.up$TG_DateNum)))


diag.up_2<- aligner(diag.up, x_diag)
contains.multiple.entries(diag.up)

ipc.up_2<- aligner(ipc.up, x_ipc)
contains.multiple.entries(ipc.up)

pzn.up_2<- aligner(pzn.up, x_pzn)
contains.multiple.entries(pzn.up)
```

```{r}
case.creating.fun<- function(ipc.data, add.data.list, start.time=0,length.of.episode,start.date="all",end.date="all"){
  #a function which generates health incidents from the data. 
  #ipc.data is the data with IPC2 codes needed for finding the patients who had coughing (IPC2 code R05) as a symptom.
  #start.time is the number of days before the patient went to their GP with coughing symptoms in which other health incidents may be recorded. It is currently redundand.
  #length.of.episode is the number of days after the patient went to their doctor for the first time that are analysed.
  #start.date is a specified TG_DateNum-value which marks the earliest date we want to analyse in the data, i.e. if we do not want to analyse all of the data but set a specific start date.
  #end.date is a specified TG_DateNum-value which marks the latest date we want to analyse in the data, i.e. if we do not want to analyse all of the data but set a specific end date.
  
  #error handles for function inputs
  if(start.date!="all"){
    if(is.numeric(start.date)){
      if(start.date<min(as.numeric(ipc.data$TG_DateNum))) warning("Start date is earlier than the earliest time in the dataset. The constraint is thus non-binding!")
    }else{
      stop("start date must be either 'all' or take a numeric value")
    }
  }
  
  if(end.date!="all"){
    if(is.numeric(end.date)){
      if(end.date<min(as.numeric(ipc.data$TG_DateNum))) warning("End date is earlier than the earliest time in the dataset. The constraint is thus non-binding!")
    }else{
      stop("End date must be either 'all' or take a numeric value")
    }
  }
  
  if(is.numeric(length.of.episode)){
    if(length.of.episode!=round(length.of.episode)) stop("length.of.episode must take an integer value!")
    if(length.of.episode>56) warning("length.of.episode is selected such that it looks at cases more than 56 days after the patient went to their GP with cough for the first time. Beware that past these eight weeks we must consider that the cough is chronic. Also beware that the longer the time frame, the higher the likelihood that medically unconnected incidents are connected by this function.")
  }else{
    stop("length.of.episode must be numeric!")
  }
  
  # 1. step: filter out all patients who never coughed
  # ...for ipc.data
  cols<- seq(1,ncol(ipc.data))[grepl("ipc2", colnames(ipc.data))]
  selector.cough<- numeric(nrow(ipc.data))
  for(i in seq(1,nrow(ipc.data))){
    ipc.string<- paste0(ipc.data[i,cols], collapse = "")
    selector.cough[i]<- grepl("R05",ipc.string)
  }
  patients.who.ever.coughed<- levels(as.factor(ipc.data$uniPatID[selector.cough]))
  ipc.data_2<- ipc.data |>
    filter(uniPatID %in% patients.who.ever.coughed)
  
  #error handle: Are there any entries in the newly created data frame?
  if(nrow(ipc.data_2)==0) stop("There are no patients who ever coughed recorded in the dataset for this configuration.")
  
  # ...for all other data sets
  
  rm.data.set<- c()
  for(i in seq(1,length(add.data.list))){
    ds<- add.data.list[[i]]|>
      filter(uniPatID %in% patients.who.ever.coughed)
    if(nrow(ds)==0){
      rm.data.set<- c(rm.data.set,i)
    }else{
      add.data.list[[i]]<- ds
    }
  }
  if(length(rm.data.set)>1){
    warning("Some data set(s) is/ are being dropped from the analysis because the patients in the dataset never went to their GP coughing.")
    add.data.list<- add.data.list[-rm.data.set]
  }
  
  #merge ipc with diag data, create cases, select cases that contain coughing, insert all into data frame, add all other information on the patients
}
```






