---
title: "12.09.23"
author: "Raphael Kroes"
date: "2023-09-12"
output: html_document
---

Procedure:
1. Clear work space & load packages
2. Read in all functions (external functions.R file)
3. Read in data
4. Preprocessing I: create correct columns
5. Check whether multiple entries for the same date/ patient are in the data sets
6. Preprocessing II: Deal with multiple entries
7. Create list of data frames
8. Merge data sets
```{r}
# 1-2
rm(list=ls())
library(dplyr)
library(parallel)
# now read in all functions from functions.R file (CTRL+A, CTRL+Enter)
```

```{r}
# 3
# Read in data
setwd("N:/StudentischeHilfskraefte/_Kroes (Christoph)/Routinedaten/01_Husten/DB")

names.vec<- c("Diag3","Impf3","IPC23","Labor3","LU3","PZN3","Stamm3","Ueberweis3")


for (i in seq(1,length(names.vec))) {
  file.name<- paste0("DB_",names.vec[i],"_v03",".csv")
  im.file<- read.csv(file = file.name, header = TRUE, sep = ";")

  assign(names.vec[i],im.file)

}
# remove duplicate file and unnecessary name
rm(file.name,im.file)

# adapt this part
ListeKrankenkassen<- read.csv(file = "ListeKrankenkassen.csv", header = TRUE, sep = ";")
```

```{r}
# 4
diag.up<- Diag3 |> 
  select(uniPatID,TG_DateNum,DiagTyp,icd10)|>
  distinct()

impf.up<- Impf3|> 
  select(uniPatID,TG_DateNum,Influenza,starts_with("Cov"))|>
  distinct()

ipc.up<- IPC23 |>
  select(uniPatID,TG_DateNum,AnamnTyp,ipc2)

labor.up<- Labor3|>
  select(uniPatID,TG_DateNum,Untersuchung,Wertnum,NormLB,NormUB) |>
  filter(Untersuchung=="KREA")
labor.up$KREA_unter<- as.numeric(labor.up$Wertnum<labor.up$NormLB)
labor.up$KREA_ueber<- as.numeric(labor.up$Wertnum>labor.up$NormUB)
labor.up<- labor.up|>
  select(uniPatID,TG_DateNum,KREA_unter,KREA_ueber)|>
  distinct()

lu.up<- LU3|> 
  select(uniPatID,TG_DateNum)|>
  distinct()
lu.up$lu.dummy<- 1

pzn.up<- PZN3 |> 
  select(uniPatID,TG_DateNum,PZN) |> 
  filter(TG_DateNum>0)|>
  distinct()

stamm.up<- Stamm3
stamm.up$PKV<- IK2PKV(stamm.up$IK)
stamm.up<- stamm.up|> 
  filter(IK>0)|>
  select(-PatID,-index_i,-IK,-Kasse,-PLZ)|>
  distinct()

ueberweis.up<- Ueberweis3|>
  select(uniPatID,TG_DateNum,Uberw_Pneumo,Uberw_Radiol,Uberw_KH) |>
  filter(Uberw_Pneumo>0|Uberw_Radiol>0|Uberw_KH>0)|>
  distinct()
```
```{r}
# 5
contains.multiple.entries(diag.up)
contains.multiple.entries(impf.up)
contains.multiple.entries(ipc.up)
contains.multiple.entries(labor.up)
contains.multiple.entries(lu.up)
contains.multiple.entries(pzn.up)
contains.multiple.entries(stamm.up)
contains.multiple.entries(ueberweis.up)

```

STOP: the difference between number of rows and patient/ time combinations must be 0. We believe diag.up, ipc.up, and pzn.up have multiple entries by design. We believe impf.up, labor.up, stamm.up, and ueberweis.up should have only one line per patient/ time combination. In #6.1 we remedy the presumed errors by selecting the last entry for each patient/ time combination. In #6.2 we write the multiple data points of diag.up, ipc.up, and pzn.up in additional columns. Both procedures leave us with unique date/ time combinations for each data set.
In #6.2, we do not keep all entries for diag.up and ipc.up. There are a few entreis with unreasonably high numbers of diagnoses or symptoms. Therefore, we truncate the number observations at the 95% quantile of the distribution of entries per combination. If the last sentence is not clear in meaning, please run the commented code to gain better insight.
```{r}
# 6.1
impf.up<- data.repair(impf.up)
contains.multiple.entries(impf.up)

labor.up<- data.repair(labor.up)
contains.multiple.entries(labor.up)

stamm.up<- data.repair(stamm.up)
contains.multiple.entries(stamm.up)

ueberweis.up<- data.repair(ueberweis.up)
contains.multiple.entries(ueberweis.up)

```
```{r}
# 6.2
x_diag<- quantile(table(paste0(diag.up$uniPatID,diag.up$TG_DateNum)), probs= 0.95)
x_ipc<- quantile(table(paste0(ipc.up$uniPatID,ipc.up$TG_DateNum)), probs= 0.95)
x_pzn<- quantile(table(paste0(pzn.up$uniPatID,pzn.up$TG_DateNum)), probs= 1)

# table(paste0(diag.up$uniPatID,diag.up$TG_DateNum)
# quantile(table(paste0(diag.up$uniPatID,diag.up$TG_DateNum)))


tic()
diag.up_2<- aligner(diag.up, x_diag)
contains.multiple.entries(diag.up)
toc()

tic()
ipc.up<- aligner(ipc.up, x_ipc)
contains.multiple.entries(ipc.up)
toc()

tic()
pzn.up<- aligner(pzn.up, x_pzn)
contains.multiple.entries(pzn.up)
toc()
```


```{r}
# 7
merger.list<- list(
  ipc.up,
  labor.up,
  ueberweis.up,
  stamm.up,
  diag.up,
  lu.up,
  impf.up,
  pzn.up
)

```

```{r}
# 8
merged.data.set<- par.patient.file(merger.list)
```





```{r}
contains.multiple.entries(trial.outcome[[1]])
```


```{r}
tic()
trial.outcome<- aligner(trial.diag, 5, TRUE)
toc()
```


```{r}
aligner<- function(df,x, debugging=FALSE, progressbar=FALSE){
  raw.combinations<- paste0(df$uniPatID,df$TG_DateNum)
  combinations<- levels(as.factor(raw.combinations))
  l<- length(combinations)
  memory<- matrix(c(combinations,rep(NA,2*l)),ncol = 3)
  colnames(memory)<- c("combination","no. seen before","last seen in row")
  
  out<- matrix(0, nrow = l, ncol = 2+x*(ncol(df)-2))
  
  ticker<- 1 #answer to "In which row in out are we right now?"
  
  partial.row<- colnames(df)!= "uniPatID" & colnames(df)!= "TG_DateNum"
  colnames(out)<- c(colnames(df),
                    paste(rep(colnames(df)[partial.row],x-1),sort(rep(1:(ncol(df)-2),x-1)),sep = "_"))
  
  if(progressbar==TRUE) {
    progress.bar<- txtProgressBar(max = nrow(df),style = 3)
    for(i in seq(1,nrow(df))){
      setTxtProgressBar(progress.bar,i)
      case<- raw.combinations[i]
      location<- which(combinations==case)

      if(is.na(memory[location,2])){
        out[ticker,1:ncol(df)]<- as.matrix(df[i,])
        memory[location,2]<- 1
        memory[location,3]<- ticker
        ticker<- ticker+1
      }else{
        no.seen<- as.numeric(memory[location,2])
        last.seen<- as.numeric(memory[location,3])
        if(no.seen<x){
          sel.col<-seq(1,ncol(df)-2)+no.seen*(ncol(df)-2)+2
          sel.data<- as.matrix(df[i,partial.row])
          out[last.seen,sel.col]<- sel.data
          memory[location,2]<- as.numeric(memory[location,2])+1
        }
      }
    }
  }else{
    for(i in seq(1,nrow(df))){
      setTxtProgressBar(progress.bar,i)
      case<- raw.combinations[i]
      location<- which(combinations==case)
  
      if(is.na(memory[location,2])){
        out[ticker,1:ncol(df)]<- as.matrix(df[i,])
        memory[location,2]<- 1
        memory[location,3]<- ticker
        ticker<- ticker+1
      }else{
        no.seen<- as.numeric(memory[location,2])
        last.seen<- as.numeric(memory[location,3])
        if(no.seen<x){
          sel.col<-seq(1,ncol(df)-2)+no.seen*(ncol(df)-2)+2
          sel.data<- as.matrix(df[i,partial.row])
          out[last.seen,sel.col]<- sel.data
          memory[location,2]<- as.numeric(memory[location,2])+1
        }
      }
    }
  }
                
  
  if(debugging==TRUE){
    return(list(as.data.frame(out),memory))
  }else{
    return(as.data.frame(out))
  }
}
```

```{r}
aligner.parallel<- function(){
  
}
```

```{r}

```



